### 2024-02-21 paper/paper.tex
Added ACL LaTeX template for paper

% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[review]{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{Instructions for *ACL Proceedings}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a separate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\begin{document}
\maketitle
\begin{abstract}
This document is a supplement to the general instructions for *ACL authors. It contains instructions for using the \LaTeX{} style files for ACL conferences. 
The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
These instructions should be used both for papers submitted for review and for final versions of accepted papers.
\end{abstract}

\section{Introduction}

These instructions are for authors submitting papers to *ACL conferences using \LaTeX. They are not self-contained. All authors must follow the general instructions for *ACL proceedings,\footnote{\url{http://acl-org.github.io/ACLPUB/formatting.html}} and this document contains additional instructions for the \LaTeX{} style files.

The templates include the \LaTeX{} source of this document (\texttt{acl.tex}),
the \LaTeX{} style file used to format it (\texttt{acl.sty}),
an ACL bibliography style (\texttt{acl\_natbib.bst}),
an example bibliography (\texttt{custom.bib}),
and the bibliography for the ACL Anthology (\texttt{anthology.bib}).

\section{Engines}

To produce a PDF file, pdf\LaTeX{} is strongly recommended (over original \LaTeX{} plus dvips+ps2pdf or dvipdf). Xe\LaTeX{} also produces PDF files, and is especially suitable for text in non-Latin scripts.

\section{Preamble}

The first line of the file must be
\begin{quote}
\begin{verbatim}
\documentclass[11pt]{article}
\end{verbatim}
\end{quote}

To load the style file in the review version:
\begin{quote}
\begin{verbatim}
\usepackage[review]{acl}
\end{verbatim}
\end{quote}
For the final version, omit the \verb|review| option:
\begin{quote}
\begin{verbatim}
\usepackage{acl}
\end{verbatim}
\end{quote}

To use Times Roman, put the following in the preamble:
\begin{quote}
\begin{verbatim}
\usepackage{times}
\end{verbatim}
\end{quote}
(Alternatives like txfonts or newtx are also acceptable.)

Please see the \LaTeX{} source of this document for comments on other packages that may be useful.

Set the title and author using \verb|\title| and \verb|\author|. Within the author list, format multiple authors using \verb|\and| and \verb|\And| and \verb|\AND|; please see the \LaTeX{} source for examples.

By default, the box containing the title and author names is set to the minimum of 5 cm. If you need more space, include the following in the preamble:
\begin{quote}
\begin{verbatim}
\setlength\titlebox{<dim>}
\end{verbatim}
\end{quote}
where \verb|<dim>| is replaced with a length. Do not set this length smaller than 5 cm.

\section{Document Body}

\subsection{Footnotes}

Footnotes are inserted with the \verb|\footnote| command.\footnote{This is a footnote.}

\subsection{Tables and figures}

See Table~\ref{tab:accents} for an example of a table and its caption.
\textbf{Do not override the default caption sizes.}

\begin{table}
\centering
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular}
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\
\hline
\end{tabular}
\caption{Example commands for accented characters, to be used in, \emph{e.g.}, Bib\TeX{} entries.}
\label{tab:accents}
\end{table}

\subsection{Hyperlinks}

Users of older versions of \LaTeX{} may encounter the following error during compilation: 
\begin{quote}
\tt\verb|\pdfendlink| ended up in different nesting level than \verb|\pdfstartlink|.
\end{quote}
This happens when pdf\LaTeX{} is used and a citation splits across a page boundary. The best way to fix this is to upgrade \LaTeX{} to 2018-12-01 or later.

\subsection{Citations}

\begin{table*}
\centering
\begin{tabular}{lll}
\hline
\textbf{Output} & \textbf{natbib command} & \textbf{ACL only command}\\
\hline
\citep{Gusfield:97} & \verb|\citep| &  \\
\citealp{Gusfield:97} & \verb|\citealp| & \\
\citet{Gusfield:97} & \verb|\citet| &  \\
  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| &  \\
  \citeposs{Gusfield:97}	&	& \verb|\citeposs|\\
\hline
\end{tabular}
\caption{\label{citation-guide}
Citation commands supported by the style file.
The style is based on the natbib package and supports all natbib citation commands.
It also supports commands defined in previous ACL style files for compatibility.
}
\end{table*}

Table~\ref{citation-guide} shows the syntax supported by the style files.
We encourage you to use the natbib styles.
You can use the command \verb|\citet| (cite in text) to get ``author (year)'' citations, like this citation to a paper by \citet{Gusfield:97}.
You can use the command \verb|\citep| (cite in parentheses) to get ``(author, year)'' citations \citep{Gusfield:97}.
You can use the command \verb|\citealp| (alternative cite without parentheses) to get ``author, year'' citations, which is useful for using citations within parentheses (e.g. \citealp{Gusfield:97}).

A possessive citation can be made with the command \verb|\citeposs|.
This is not a standard natbib command, so it is generally not compatible
with other style files.

\subsection{References}

\nocite{Ando2005,andrew2007scalable,rasooli-tetrault-2015}

The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
If your own bib file is named \texttt{custom.bib}, then placing the following before any appendices in your \LaTeX{} file will generate the references section for you:
\begin{quote}
\begin{verbatim}
\bibliography{custom}
\end{verbatim}
\end{quote}

You can obtain the complete ACL Anthology as a Bib\TeX{} file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
To include both the Anthology and your own .bib file, use the following instead of the above.
\begin{quote}
\begin{verbatim}
\bibliography{anthology,custom}
\end{verbatim}
\end{quote}

Please see Section~\ref{sec:bibtex} for information on preparing Bib\TeX{} files.

\subsection{Appendices}

Use \verb|\appendix| before any appendix section to switch the section numbering over to letters. See Appendix~\ref{sec:appendix} for an example.

\section{Bib\TeX{} Files}
\label{sec:bibtex}

Unicode cannot be used in Bib\TeX{} entries, and some ways of typing special characters can disrupt Bib\TeX's alphabetization. The recommended way of typing special characters is shown in Table~\ref{tab:accents}.

Please ensure that Bib\TeX{} records contain DOIs or URLs when possible, and for all the ACL materials that you reference.
Use the \verb|doi| field for DOIs and the \verb|url| field for URLs.
If a Bib\TeX{} entry has a URL or DOI field, the paper title in the references section will appear as a hyperlink to the paper, using the hyperref \LaTeX{} package.

\section*{Acknowledgements}

This document has been adapted
by Steven Bethard, Ryan Cotterell and Rui Yan
from the instructions for earlier ACL and NAACL proceedings, including those for 
ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
NAACL 2019 by Stephanie Lukin and Alla Roskovskaya, 
ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
NAACL 2018 by Margaret Mitchell and Stephanie Lukin,
Bib\TeX{} suggestions for (NA)ACL 2017/2018 from Jason Eisner,
ACL 2017 by Dan Gildea and Min-Yen Kan, 
NAACL 2017 by Margaret Mitchell, 
ACL 2012 by Maggie Li and Michael White, 
ACL 2010 by Jing-Shin Chang and Philipp Koehn, 
ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
ACL 2002 by Eugene Charniak and Dekang Lin, 
and earlier ACL and EACL formats written by several people, including
John Chen, Henry S. Thompson and Donald Walker.
Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.

% Bibliography entries for the entire Anthology, followed by custom entries
%\bibliography{anthology,custom}
% Custom bibliography entries only
\bibliography{sources}

\appendix

\section{Example Appendix}
\label{sec:appendix}

This is an appendix.

\end{document}

### 2024-04-22 paper/paper.tex
Fixed tracking problem and constructed basic template for thesis

@@
 % Change to "preprint" to generate a non-anonymous version with page numbers.
-\usepackage[review]{acl}
+\usepackage[preprint]{acl}
 
@@
 
-\title{Instructions for *ACL Proceedings}
+\title{(Automatic) Speech Recognition --- Project}
 
-% Author information can be set in various styles:
-% For several authors from the same institution:
-% \author{Author 1 \and ... \and Author n \\
-%         Address line \\ ... \\ Address line}
-% if the names do not fit well on one line use
-%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
-% For authors from different institutions:
-% \author{Author 1 \\ Address line \\  ... \\ Address line
-%         \And  ... \And
-%         Author n \\ Address line \\ ... \\ Address line}
-% To start a separate ``row'' of authors use \AND, as in
-% \author{Author 1 \\ Address line \\  ... \\ Address line
-%         \AND
-%         Author 2 \\ Address line \\ ... \\ Address line \And
-%         Author 3 \\ Address line \\ ... \\ Address line}
-
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  \texttt{email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  \texttt{email@domain} \\}
+\author{Daan Brugmans \\
+  Radboud University\\
+  \texttt{daan.brugmans@ru.nl}
+}
 
 \begin{document}
+
 \maketitle
-\begin{abstract}
-This document is a supplement to the general instructions for *ACL authors. It contains instructions for using the \LaTeX{} style files for ACL conferences. 
-The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
-These instructions should be used both for papers submitted for review and for final versions of accepted papers.
-\end{abstract}
 
@@
 
-These instructions are for authors submitting papers to *ACL conferences using \LaTeX.
-They are not self-contained.
-All authors must follow the general instructions for *ACL proceedings,\footnote{\url{http://acl-org.github.io/ACLPUB/formatting.html}} and this document contains additional instructions for the \LaTeX{} style files.
+\section{Related Work}
 
-The templates include the \LaTeX{} source of this document (\texttt{acl.tex}),
-the \LaTeX{} style file used to format it (\texttt{acl.sty}),
-an ACL bibliography style (\texttt{acl\_natbib.bst}),
-an example bibliography (\texttt{custom.bib}),
-and the bibliography for the ACL Anthology (\texttt{anthology.bib}).
+\section{Method}
 
-\section{Engines}
+\section{Experiment}
 
-To produce a PDF file, pdf\LaTeX{} is strongly recommended (over original \LaTeX{} plus dvips+ps2pdf or dvipdf).
-Xe\LaTeX{} also produces PDF files, and is especially suitable for text in non-Latin scripts.
+\section{Results}
 
-\section{Preamble}
+\section{Discussion}
 
-The first line of the file must be
-\begin{quote}
-\begin{verbatim}
-\documentclass[11pt]{article}
-\end{verbatim}
-\end{quote}
+\section{Conclusion}
 
-To load the style file in the review version:
-\begin{quote}
-\begin{verbatim}
-\usepackage[review]{acl}
-\end{verbatim}
-\end{quote}
-For the final version, omit the \verb|review| option:
-\begin{quote}
-\begin{verbatim}
-\usepackage{acl}
-\end{verbatim}
-\end{quote}
-
-To use Times Roman, put the following in the preamble:
-\begin{quote}
-\begin{verbatim}
-\usepackage{times}
-\end{verbatim}
-\end{quote}
-(Alternatives like txfonts or newtx are also acceptable.)
-
-Please see the \LaTeX{} source of this document for comments on other packages that may be useful.
-
-Set the title and author using \verb|\title| and \verb|\author|.
-Within the author list, format multiple authors using \verb|\and| and \verb|\And| and \verb|\AND|; please see the \LaTeX{} source for examples.
-
-By default, the box containing the title and author names is set to the minimum of 5 cm. If you need more space, include the following in the preamble:
-\begin{quote}
-\begin{verbatim}
-\setlength\titlebox{<dim>}
-\end{verbatim}
-\end{quote}
-where \verb|<dim>| is replaced with a length. Do not set this length smaller than 5 cm.
-
-\section{Document Body}
-
-\subsection{Footnotes}
-
-Footnotes are inserted with the \verb|\footnote| command.\footnote{This is a footnote.}
-
-\subsection{Tables and figures}
-
-See Table~\ref{tab:accents} for an example of a table and its caption.
-\textbf{Do not override the default caption sizes.}
-
-\begin{table}
-\centering
-\begin{tabular}{lc}
-\hline
-\textbf{Command} & \textbf{Output}\\
-\hline
-\verb|{\"a}| & {\"a} \\
-\verb|{\^e}| & {\^e} \\
-\verb|{\`i}| & {\`i} \\ 
-\verb|{\.I}| & {\.I} \\ 
-\verb|{\o}| & {\o} \\
-\verb|{\'u}| & {\'u}  \\ 
-\verb|{\aa}| & {\aa}  \\\hline
-\end{tabular}
-\begin{tabular}{lc}
-\hline
-\textbf{Command} & \textbf{Output}\\
-\hline
-\verb|{\c c}| & {\c c} \\ 
-\verb|{\u g}| & {\u g} \\ 
-\verb|{\l}| & {\l} \\ 
-\verb|{\~n}| & {\~n} \\ 
-\verb|{\H o}| & {\H o} \\ 
-\verb|{\v r}| & {\v r} \\ 
-\verb|{\ss}| & {\ss} \\
-\hline
-\end{tabular}
-\caption{Example commands for accented characters, to be used in, \emph{e.g.}, Bib\TeX{} entries.}
-\label{tab:accents}
-\end{table}
-
-\subsection{Hyperlinks}
-
-Users of older versions of \LaTeX{} may encounter the following error during compilation: 
-\begin{quote}
-\tt\verb|\pdfendlink| ended up in different nesting level than \verb|\pdfstartlink|.
-\end{quote}
-This happens when pdf\LaTeX{} is used and a citation splits across a page boundary. The best way to fix this is to upgrade \LaTeX{} to 2018-12-01 or later.
-
-\subsection{Citations}
-
-\begin{table*}
-\centering
-\begin{tabular}{lll}
-\hline
-\textbf{Output} & \textbf{natbib command} & \textbf{ACL only command}\\
-\hline
-\citep{Gusfield:97} & \verb|\citep| &  \\
-\citealp{Gusfield:97} & \verb|\citealp| & \\
-\citet{Gusfield:97} & \verb|\citet| &  \\
-  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| &  \\
-  \citeposs{Gusfield:97}	&	& \verb|\citeposs|\\
-\hline
-\end{tabular}
-\caption{\label{citation-guide}
-Citation commands supported by the style file.
-The style is based on the natbib package and supports all natbib citation commands.
-It also supports commands defined in previous ACL style files for compatibility.
-}
-\end{table*}
-
-Table~\ref{citation-guide} shows the syntax supported by the style files.
-We encourage you to use the natbib styles.
-You can use the command \verb|\citet| (cite in text) to get ``author (year)'' citations, like this citation to a paper by \citet{Gusfield:97}.
-You can use the command \verb|\citep| (cite in parentheses) to get ``(author, year)'' citations \citep{Gusfield:97}.
-You can use the command \verb|\citealp| (alternative cite without parentheses) to get ``author, year'' citations, which is useful for using citations within parentheses (e.g. \citealp{Gusfield:97}).
-
-A possessive citation can be made with the command \verb|\citeposs|.
-This is not a standard natbib command, so it is generally not compatible
-with other style files.
-
-\subsection{References}
-
-\nocite{Ando2005,andrew2007scalable,rasooli-tetrault-2015}
-
-The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
-If your own bib file is named \texttt{custom.bib}, then placing the following before any appendices in your \LaTeX{} file will generate the references section for you:
-\begin{quote}
-\begin{verbatim}
 \bibliography{custom}
-\end{verbatim}
-\end{quote}
-
-You can obtain the complete ACL Anthology as a Bib\TeX{} file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
-To include both the Anthology and your own .bib file, use the following instead of the above.
-\begin{quote}
-\begin{verbatim}
-\bibliography{anthology,custom}
-\end{verbatim}
-\end{quote}
-
-Please see Section~\ref{sec:bibtex} for information on preparing Bib\TeX{} files.
-
-\subsection{Appendices}
-
-Use \verb|\appendix| before any appendix section to switch the section numbering over to letters. See Appendix~\ref{sec:appendix} for an example.
-
-\section{Bib\TeX{} Files}
-\label{sec:bibtex}
-
-Unicode cannot be used in Bib\TeX{} entries, and some ways of typing special characters can disrupt Bib\TeX's alphabetization.
-The recommended way of typing special characters is shown in Table~\ref{tab:accents}.
-
-Please ensure that Bib\TeX{} records contain DOIs or URLs when possible, and for all the ACL materials that you reference.
-Use the \verb|doi| field for DOIs and the \verb|url| field for URLs.
-If a Bib\TeX{} entry has a URL or DOI field, the paper title in the references section will appear as a hyperlink to the paper, using the hyperref \LaTeX{} package.
-
-\section*{Acknowledgements}
-
-This document has been adapted
-by Steven Bethard, Ryan Cotterell and Rui Yan
-from the instructions for earlier ACL and NAACL proceedings, including those for 
-ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
-NAACL 2019 by Stephanie Lukin and Alla Roskovskaya, 
-ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
-NAACL 2018 by Margaret Mitchell and Stephanie Lukin,
-Bib\TeX{} suggestions for (NA)ACL 2017/2018 from Jason Eisner,
-ACL 2017 by Dan Gildea and Min-Yen Kan, 
-NAACL 2017 by Margaret Mitchell, 
-ACL 2012 by Maggie Li and Michael White, 
-ACL 2010 by Jing-Shin Chang and Philipp Koehn, 
-ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
-ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
-ACL 2002 by Eugene Charniak and Dekang Lin, 
-and earlier ACL and EACL formats written by several people, including
-John Chen, Henry S. Thompson and Donald Walker.
-Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.
-
-% Bibliography entries for the entire Anthology, followed by custom entries
-%\bibliography{anthology,custom}
-% Custom bibliography entries only
-\bibliography{sources}
 
@@
 
-\section{Example Appendix}
-\label{sec:appendix}
-
-This is an appendix.
-
 \end{document}

### 2024-04-22 paper/template/acl_template.tex
Added citation for relevant paper

% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[review]{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{Instructions for *ACL Proceedings}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a separate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\begin{document}
\maketitle
\begin{abstract}
This document is a supplement to the general instructions for *ACL authors. It contains instructions for using the \LaTeX{} style files for ACL conferences. 
The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
These instructions should be used both for papers submitted for review and for final versions of accepted papers.
\end{abstract}

\section{Introduction}

These instructions are for authors submitting papers to *ACL conferences using \LaTeX. They are not self-contained. All authors must follow the general instructions for *ACL proceedings,\footnote{\url{http://acl-org.github.io/ACLPUB/formatting.html}} and this document contains additional instructions for the \LaTeX{} style files.

The templates include the \LaTeX{} source of this document (\texttt{acl.tex}),
the \LaTeX{} style file used to format it (\texttt{acl.sty}),
an ACL bibliography style (\texttt{acl\_natbib.bst}),
an example bibliography (\texttt{custom.bib}),
and the bibliography for the ACL Anthology (\texttt{anthology.bib}).

\section{Engines}

To produce a PDF file, pdf\LaTeX{} is strongly recommended (over original \LaTeX{} plus dvips+ps2pdf or dvipdf). Xe\LaTeX{} also produces PDF files, and is especially suitable for text in non-Latin scripts.

\section{Preamble}

The first line of the file must be
\begin{quote}
\begin{verbatim}
\documentclass[11pt]{article}
\end{verbatim}
\end{quote}

To load the style file in the review version:
\begin{quote}
\begin{verbatim}
\usepackage[review]{acl}
\end{verbatim}
\end{quote}
For the final version, omit the \verb|review| option:
\begin{quote}
\begin{verbatim}
\usepackage{acl}
\end{verbatim}
\end{quote}

To use Times Roman, put the following in the preamble:
\begin{quote}
\begin{verbatim}
\usepackage{times}
\end{verbatim}
\end{quote}
(Alternatives like txfonts or newtx are also acceptable.)

Please see the \LaTeX{} source of this document for comments on other packages that may be useful.

Set the title and author using \verb|\title| and \verb|\author|. Within the author list, format multiple authors using \verb|\and| and \verb|\And| and \verb|\AND|; please see the \LaTeX{} source for examples.

By default, the box containing the title and author names is set to the minimum of 5 cm. If you need more space, include the following in the preamble:
\begin{quote}
\begin{verbatim}
\setlength\titlebox{<dim>}
\end{verbatim}
\end{quote}
where \verb|<dim>| is replaced with a length. Do not set this length smaller than 5 cm.

\section{Document Body}

\subsection{Footnotes}

Footnotes are inserted with the \verb|\footnote| command.\footnote{This is a footnote.}

\subsection{Tables and figures}

See Table~\ref{tab:accents} for an example of a table and its caption.
\textbf{Do not override the default caption sizes.}

\begin{table}
\centering
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular}
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\
\hline
\end{tabular}
\caption{Example commands for accented characters, to be used in, \emph{e.g.}, Bib\TeX{} entries.}
\label{tab:accents}
\end{table}

\subsection{Hyperlinks}

Users of older versions of \LaTeX{} may encounter the following error during compilation: 
\begin{quote}
\tt\verb|\pdfendlink| ended up in different nesting level than \verb|\pdfstartlink|.
\end{quote}
This happens when pdf\LaTeX{} is used and a citation splits across a page boundary. The best way to fix this is to upgrade \LaTeX{} to 2018-12-01 or later.

\subsection{Citations}

\begin{table*}
\centering
\begin{tabular}{lll}
\hline
\textbf{Output} & \textbf{natbib command} & \textbf{ACL only command}\\
\hline
\citep{Gusfield:97} & \verb|\citep| &  \\
\citealp{Gusfield:97} & \verb|\citealp| & \\
\citet{Gusfield:97} & \verb|\citet| &  \\
  \citeyearpar{Gusfield:97} & \verb|\citeyearpar| &  \\
  \citeposs{Gusfield:97}	&	& \verb|\citeposs|\\
\hline
\end{tabular}
\caption{\label{citation-guide}
Citation commands supported by the style file.
The style is based on the natbib package and supports all natbib citation commands.
It also supports commands defined in previous ACL style files for compatibility.
}
\end{table*}

Table~\ref{citation-guide} shows the syntax supported by the style files.
We encourage you to use the natbib styles.
You can use the command \verb|\citet| (cite in text) to get ``author (year)'' citations, like this citation to a paper by \citet{Gusfield:97}.
You can use the command \verb|\citep| (cite in parentheses) to get ``(author, year)'' citations \citep{Gusfield:97}.
You can use the command \verb|\citealp| (alternative cite without parentheses) to get ``author, year'' citations, which is useful for using citations within parentheses (e.g. \citealp{Gusfield:97}).

A possessive citation can be made with the command \verb|\citeposs|.
This is not a standard natbib command, so it is generally not compatible
with other style files.

\subsection{References}

\nocite{Ando2005,andrew2007scalable,rasooli-tetrault-2015}

The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
If your own bib file is named \texttt{custom.bib}, then placing the following before any appendices in your \LaTeX{} file will generate the references section for you:
\begin{quote}
\begin{verbatim}
\bibliography{custom}
\end{verbatim}
\end{quote}

You can obtain the complete ACL Anthology as a Bib\TeX{} file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
To include both the Anthology and your own .bib file, use the following instead of the above.
\begin{quote}
\begin{verbatim}
\bibliography{anthology,custom}
\end{verbatim}
\end{quote}

Please see Section~\ref{sec:bibtex} for information on preparing Bib\TeX{} files.

\subsection{Appendices}

Use \verb|\appendix| before any appendix section to switch the section numbering over to letters. See Appendix~\ref{sec:appendix} for an example.

\section{Bib\TeX{} Files}
\label{sec:bibtex}

Unicode cannot be used in Bib\TeX{} entries, and some ways of typing special characters can disrupt Bib\TeX's alphabetization. The recommended way of typing special characters is shown in Table~\ref{tab:accents}.

Please ensure that Bib\TeX{} records contain DOIs or URLs when possible, and for all the ACL materials that you reference.
Use the \verb|doi| field for DOIs and the \verb|url| field for URLs.
If a Bib\TeX{} entry has a URL or DOI field, the paper title in the references section will appear as a hyperlink to the paper, using the hyperref \LaTeX{} package.

\section*{Acknowledgements}

This document has been adapted
by Steven Bethard, Ryan Cotterell and Rui Yan
from the instructions for earlier ACL and NAACL proceedings, including those for 
ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
NAACL 2019 by Stephanie Lukin and Alla Roskovskaya, 
ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
NAACL 2018 by Margaret Mitchell and Stephanie Lukin,
Bib\TeX{} suggestions for (NA)ACL 2017/2018 from Jason Eisner,
ACL 2017 by Dan Gildea and Min-Yen Kan, 
NAACL 2017 by Margaret Mitchell, 
ACL 2012 by Maggie Li and Michael White, 
ACL 2010 by Jing-Shin Chang and Philipp Koehn, 
ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
ACL 2002 by Eugene Charniak and Dekang Lin, 
and earlier ACL and EACL formats written by several people, including
John Chen, Henry S. Thompson and Donald Walker.
Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.

% Bibliography entries for the entire Anthology, followed by custom entries
%\bibliography{anthology,custom}
% Custom bibliography entries only
\bibliography{custom}

\appendix

\section{Example Appendix}
\label{sec:appendix}

This is an appendix.

\end{document}

### 2024-05-26 paper/paper.tex
Added citation for relevant paper
Wrote introduction

@@
 
-\title{(Automatic) Speech Recognition --- Project}
+\title{Attacks on Neural Networks in a Lightweight Speech Anonymization Pipeline}
 
@@
 
+\begin{abstract}
+
+\end{abstract}
+
 \section{Introduction}
+As advancements in the field of Automatic Speech Recognition (ASR) have accelerated with the rise of modern End-to-End neural networks, the risks associated with using such models in ASR applications has become more evident.
+
+Modern neural ASR models are capable of parsing and producing speech to a new level of authenticity: transformers are State-of-the-Art for ASR and word recognition, and the introduction of modern unsupervised deep neural network architectures, such as Generative Adversarial Networks (GANs) and Variational Autoencoders (VAEs), has allowed for more realistic, accurate, and easier generation of speech.
+These modern speech generation models are capable of learning to reproduce a person's voice, and then generating new speech using the learned voice.
+Such synthesized speeches are called \textit{deepfaked} speeches, or simply \textit{deepfakes}.
+
+The presence and influence of deepfakes has become increasingly apparent in recent years: neurally synthesized audio and video of important persons are used to spread misinformation and manipulate.
+One way to counteract the repercussions of deepfakes is the removal of the personalization in the learned, and thus reproduced, speech.
+This is called \textit{Speaker Anonymization}.
+In Speaker Anonymization, we aim to maintain the ASR quality of the audio, while applying changes that make the audio untraceable to a person's likeness.
+
+Although modern Speaker Anonymization systems, often neural in nature, have been shown to be able to anonymize speech while maintaining ASR quality, they can also be manipulated.
+By attacking neural Speaker Anonymization systems, we may be able to circumvent the preventative measures they provide, and generate speech to a person's likeness regardless of their presence.
+This paper will focus in that topic: attacking neural Speaker Anonymization systems.
 
 \section{Related Work}
+\citet{meyer2023anonymizing}
 

### 2024-05-26 paper/paper.tex
Collected sources

@@
 
+\usepackage{natbib}
+
 \title{Attacks on Neural Networks in a Lightweight Speech Anonymization Pipeline}
@@
 \section{Related Work}
-\citet{meyer2023anonymizing}
+\citet{meyer2023anonymizing} % Work on neural speaker anonymization
+
+\citet{shihao2024adversarial} % Work on attacking neural speaker anonymization
+
+\citet{xiaoyong2019adversarial} % Often cited paper about adversarial examples and attacks, use for introducing the idea of attacks on neural networks
+
+\citet{goodfellow2015explaining} % The paper about FGSM, use as intro to evasion attacks
+
+\citet{madry2018towards} % The paper about PGD, which we will use, builds upon FGSM
+
+\citet{gu2019badnets} % The paper about BadNets. Keep it brief. Use it to visualize the backdooring process.
+
+\citet{liu2018trojaning} % The paper about trojanning audio. Keep it brief. Use it to show that backdooring audio is also possible.
+
+\citet{stefanos2022ultrasonic} % The paper about ultrasonic frequencies for backdooring. Keep it brief. Another example of audio backdoor.
+
+\citet{stefanos2023jingleback} % Jingleback paper. Explain in more details since you will focus on it.
 
 \section{Method}
+\citet{kai2022lightweight} % Work on lightweight speaker anonymization, idea for our method/pipeline.
 

### 2024-05-26 paper/paper.tex
Wrote related work section for neural speaker anonymization and evasion attacks

@@
 \usepackage{natbib}
+\usepackage{url}
+\usepackage{hyperref}
+\usepackage{graphicx}
+\usepackage{amsmath}
+
+\graphicspath{{./images}}
 
@@
 \maketitle
+% \begin{table}
+%     \centering
+%     \begin{tabular}{cols}
+
+%     \end{tabular}
+%     \caption{}
+%     \label{tab:}
+% \end{table}
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.9\textwidth]{}
+%     \caption{}
+%     \label{fig:}
+% \end{figure}
 
@@
 
-Although modern Speaker Anonymization systems, often neural in nature, have been shown to be able to anonymize speech while maintaining ASR quality, they can also be manipulated.
+Although modern Speaker Anonymization systems, often neural in nature, have been shown to be able to anonymize speech while maintaining ASR quality, they themselves can also be manipulated.
 By attacking neural Speaker Anonymization systems, we may be able to circumvent the preventative measures they provide, and generate speech to a person's likeness regardless of their presence.
 This paper will focus in that topic: attacking neural Speaker Anonymization systems.
+Specifically, we will focus on the topic of adversarial attacks.
+\textit{Adversarial attacks} on deep neural networks are attacks that alter the input that the network receives.
+They are performed by applying a perturbation onto the input data with the aim to alter or manipulate the network's behavior.
+These perturbations should meet two criteria as faithfully as possible: they should not be detectable by humans and they should perturb the original input as little as possible.
 
 \section{Related Work}
-\citet{meyer2023anonymizing} % Work on neural speaker anonymization
+\subsection{Neural Speaker Anonymization}
+\citet{meyer2023anonymizing} showcase a successful realization of neural Speaker Anonymization using GANs.
+Their Speaker Anonymization architecture includes the extraction of embeddings from speech, which are fed into a GAN.
+This GAN first learns to generate embeddings sampled from a normal distribution.
+After every sampling step, it then learns to calculate the distance between the embedding that it generated, and an embeddings extracted from speech it has been fed.
+This training procedure teaches the GAN to generate embeddings that are similar to the speech embeddings.
+Once training has been finished, embeddings based on real speech embeddings are sampled from the GAN until an embedding is generated whose cosine distance from the corresponding real speech embeddings is sufficiently large.
+This embedding is fed to an existing speech synthesis model, which produces anonymized speech.
 
-\citet{shihao2024adversarial} % Work on attacking neural speaker anonymization
+\citet{shihao2024adversarial} showcase another example of a neural Speaker Anonymization pipeline.
+Their main contribution is the use of an \textit{adversarial attack} for anonymization purposes.
+\citeauthor{shihao2024adversarial} use an adversarial attack called \textit{FGSM} that learns to apply perturbations on a VAE's latent space vector that represents a personalized utterance.
+The perturbations caused by the FGSM attack alter the latent space vector in such a way that it is as far removed from the original speaker as possible, while still being recognizable.
+When the vector is then fed to the VAE's decoder, it is unable to extract features from the perturbed vector that relate to the original speaker's speech characterizations.
+The resulting decoded speech sample is thus anonymous.
 
-\citet{xiaoyong2019adversarial} % Often cited paper about adversarial examples and attacks, use for introducing the idea of attacks on neural networks
+\subsection{Attacks on Neural Networks}
+The FGSM attack used by \citet{shihao2024adversarial} is an example of an adversarial attack.
+Adversarial attacks are extensively described by \citet{xiaoyong2019adversarial}.
+They provide an introduction to and an overview of adversarial attacks within the deep learning domain, and should provide the reader with plentiful knowledge on the topic.
 
-\citet{goodfellow2015explaining} % The paper about FGSM, use as intro to evasion attacks
+We will focus on two types of adversarial attacks: \textit{Evasion Attacks} and \textit{Backdoor Attacks}.
 
-\citet{madry2018towards} % The paper about PGD, which we will use, builds upon FGSM
+\subsubsection{Evasion Attacks}
+Evasion attacks are adversarial attacks that are used during model inference.
+The aim of an evasion attack is to perturb an input in such a way that a fully trained model is fooled into behaving differently.
+This behavior should fulfill the attacker's goals.
 
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.45\textwidth]{fgsm.png}
+    \caption{An example of an FGSM attack visualized \citep{goodfellow2015explaining}.}
+    \label{fig:fgsm}
+\end{figure}
+
+\citet{goodfellow2015explaining} introduced FGSM, the \textit{Fast Gradient Sign Method}.
+FGSM perturbs the input by exploiting a trained model's gradients.
+When given the input $x$ and its label $y$, an FGSM attack calculates the gradient with respect to the input using the model's parameters $\theta$ and loss function $J(\theta, x, y)$.
+The sign of this gradient is calculated and is added on top of the original input by a factor of $\epsilon$.
+The FGSM attack can then be defined as such:
+\begin{align*}
+  x_t &= x + \epsilon \cdot \text{sign}(\nabla_x J(\theta, x, y))
+\end{align*}
+where $x_t$ is the perturbed input.
+A visualization of this process can be found in figure \ref{fig:fgsm}.
+
+FGSM attacks have some limitations.
+One of these limitations is that an FGSM attack is a one-step approach: the gradient with respect to the input is calculated once, and is then used immediately with to corrective measures.
+Although this makes FGSM attacks cheap, it also makes the attack difficult to perform optimally.
+\citet{madry2018towards} propose an expanded version of the FGSM attack called the \textit{Projected Gradient Descent} (PGD) method.
+The core principle of PGD is that it projects FGSM gradients back to a predefined max perturbation level; if an FGSM's perturbation is too big, PGD projects it back.
+This makes PGD a multiple-step approach.
+
+PGD's projection of an FGSM attack is performed by applying a clipping function $\text{clip}()$ on the FGSM attack.
+The clipping function will clip gradients outside the limit of $x + S$, where $x$ is the original input data and $S$ is the predefined maximal Euclidean distance a perturbation is allowed to be from $x$.
+Prior to clipping the FGSM perturbed input $x_t$, PGD will apply another FGSM attack on the model, but will now calculate the gradient with respect to the perturbed input $x_t$ instead of the original input $x$.
+This additional FGSM attack is added onto $x_t$ by a factor of hyperparameter $\alpha$.
+It is the result of this addition that is clipped by the clipping function.
+This means that a PGD attack can be defined as follows:
+\begin{align*}
+  x_t &= x + \epsilon \cdot \text{sign}(\nabla_x J(\theta, x, y)) \\
+  x_{t+1} &= \text{clip}_{x + S}(x_t + \alpha \cdot \text{sign}(\nabla_x J(\theta, x_t, y)))
+\end{align*}
+where $x_{t+1}$ is the final result of one round of PGD.
+PGD can be performed for multiple rounds $T$ until $x_T$ is reached.
+
+\subsubsection{Backdoor Attacks}
 \citet{gu2019badnets} % The paper about BadNets. Keep it brief. Use it to visualize the backdooring process.
@@
 \citet{stefanos2023jingleback} % Jingleback paper. Explain in more details since you will focus on it.
+
+\subsection{Attacks on Neural Speech Systems}
+\citet{neekhara2019universal} % Paper about adversarial attacks on ASR systems
+
+\citet{kreuk2018fooling} % Paper about adversarial attacks on E2E speaker verification
 

### 2024-05-26 paper/paper.tex
Started writing related works for backdoor attacks

@@
 
-\title{Attacks on Neural Networks in a Lightweight Speech Anonymization Pipeline}
+\title{(Automatic) Speech Recognition Project --- Attacks on Neural Networks in a Lightweight Speech Anonymization Pipeline}
 
@@
 \subsubsection{Backdoor Attacks}
-\citet{gu2019badnets} % The paper about BadNets. Keep it brief. Use it to visualize the backdooring process.
+Backdoor attacks are adversarial attacks that are used during model training.
+They are a subset of \textit{Poisoning Attacks}.
+The aim of a poisoning attack is to alter (a subset of) the training data in order to teach the model certain behavior or to decrease the model's performance.
+Backdoor attacks are a specific type of poisoning attack where the attacker teaches a model to respond to a certain property of the data.
+If the model encounters that property in a data sample, it should behave according to the attacker's goals.
+This property is called a \textit{trigger}.
 
+\begin{figure*}[h]
+  \centering
+  \includegraphics[width=0.9\textwidth]{badnet.png}
+  \caption{An example of a BadNet attack \citep{gu2019badnets}.
+On the left, an image of a stop sign with varying BadNet backdoors can be seen.
+On the right, a backdoored network can be seen interpreting a stop sign as a speed limit sign due to the physical backdoor on the sign itself.}
+  \label{fig:badnet}
+\end{figure*}
+
+A well-known example of a backdoor attack is the BadNet attack by \citet{gu2019badnets}.
+BadNet attacks poison a dataset of images by adding a visual feature onto the image, such as a colored square.
+A Convolutional Neural Network (CNN) will then learn to associate the visual feature with certain behavior.
+If the model has successfully learned to associate the trigger with certain behavior, then it will display that behavior during inference when given an image with the trigger, such as misclassifying an image.
+
+Since backdoor attacks are applied during training, certain attacks can only be used on certain types of data and networks.
+Although backdoor attacks are most often used on image data, there also exist backdoor attacks on audio data.
+\dots % Ga hier door!
 \citet{liu2018trojaning} % The paper about trojanning audio. Keep it brief. Use it to show that backdooring audio is also possible.
-
 \citet{stefanos2022ultrasonic} % The paper about ultrasonic frequencies for backdooring. Keep it brief. Another example of audio backdoor.
 
+% Nieuwe alinea
 \citet{stefanos2023jingleback} % Jingleback paper. Explain in more details since you will focus on it.

### 2024-05-27 paper/paper.tex
Proofread and improved previous text

@@
 \section{Introduction}
-As advancements in the field of Automatic Speech Recognition (ASR) have accelerated with the rise of modern End-to-End neural networks, the risks associated with using such models in ASR applications has become more evident.
+As advancements in the field of Automatic Speech Recognition (ASR) have accelerated with the rise of modern end-to-end neural networks, the risks associated with using such models in ASR applications has become more evident.
 
-Modern neural ASR models are capable of parsing and producing speech to a new level of authenticity: transformers are State-of-the-Art for ASR and word recognition, and the introduction of modern unsupervised deep neural network architectures, such as Generative Adversarial Networks (GANs) and Variational Autoencoders (VAEs), has allowed for more realistic, accurate, and easier generation of speech.
-These modern speech generation models are capable of learning to reproduce a person's voice, and then generating new speech using the learned voice.
-Such synthesized speeches are called \textit{deepfaked} speeches, or simply \textit{deepfakes}.
+Modern neural ASR models are capable of parsing and producing speech to a new level of authenticity: transformers are state-of-the-art for ASR and word recognition, and the introduction of modern unsupervised deep neural network architectures, such as Generative Adversarial Networks (GANs) and Variational Autoencoders (VAEs), has allowed for more realistic, accurate, and easier generation of speech.
+These modern speech generation models are capable of learning to reproduce a person's voice, and then generating new utterances using the learned voice.
+Such synthesized utterances are called \textit{deepfaked} utterances, or simply \textit{deepfakes}.
 
-The presence and influence of deepfakes has become increasingly apparent in recent years: neurally synthesized audio and video of important persons are used to spread misinformation and manipulate.
-One way to counteract the repercussions of deepfakes is the removal of the personalization in the learned, and thus reproduced, speech.
+The presence and influence of deepfakes has become increasingly apparent in recent years: neurally synthesized audio and video of real persons are used to spread misinformation and to manipulate.
+This recent development has raised attention on the development of methods that prevent or complicate the production of deepfakes.
+One way to complicate the production of deepfakes is the removal of characteristics in the audio that relate to the speaker's likeness.
 This is called \textit{Speaker Anonymization}.
-In Speaker Anonymization, we aim to maintain the ASR quality of the audio, while applying changes that make the audio untraceable to a person's likeness.
+In Speaker Anonymization, we aim to apply changes to a speaker's utterance such that the changes mde make the utterance untraceable to the person's likeness, while understandability is maintained.
 
-Although modern Speaker Anonymization systems, often neural in nature, have been shown to be able to anonymize speech while maintaining ASR quality, they themselves can also be manipulated.
-By attacking neural Speaker Anonymization systems, we may be able to circumvent the preventative measures they provide, and generate speech to a person's likeness regardless of their presence.
+Modern Speaker Anonymization systems, often neural in nature, have been shown to be able to anonymize speech while maintaining understandability.
+However, such neural systems are not impenetrable, and there exist many sorts of attacks aimed at neural networks.
+By attacking neural Speaker Anonymization systems, we may be able to circumvent the preventative measures they provide, and generate speech to a person's likeness nonetheless.
 This paper will focus in that topic: attacking neural Speaker Anonymization systems.
@@
 This GAN first learns to generate embeddings sampled from a normal distribution.
-After every sampling step, it then learns to calculate the distance between the embedding that it generated, and an embeddings extracted from speech it has been fed.
+After every sample, it then learns to calculate the distance between the embedding that it generated, and an embedding extracted from speech it has been fed.
 This training procedure teaches the GAN to generate embeddings that are similar to the speech embeddings.
 Once training has been finished, embeddings based on real speech embeddings are sampled from the GAN until an embedding is generated whose cosine distance from the corresponding real speech embeddings is sufficiently large.
+If the cosine distance is sufficiently large, the GAN should have produced an embedding that represents the contents of the speech utterance without representing the characteristics of the speaker found in the utterance.
 This embedding is fed to an existing speech synthesis model, which produces anonymized speech.
@@
 \citet{shihao2024adversarial} showcase another example of a neural Speaker Anonymization pipeline.
-Their main contribution is the use of an \textit{adversarial attack} for anonymization purposes.
-\citeauthor{shihao2024adversarial} use an adversarial attack called \textit{FGSM} that learns to apply perturbations on a VAE's latent space vector that represents a personalized utterance.
-The perturbations caused by the FGSM attack alter the latent space vector in such a way that it is as far removed from the original speaker as possible, while still being recognizable.
-When the vector is then fed to the VAE's decoder, it is unable to extract features from the perturbed vector that relate to the original speaker's speech characterizations.
-The resulting decoded speech sample is thus anonymous.
+Their main contribution is the use of an adversarial attack for anonymization purposes.
+\citeauthor{shihao2024adversarial} use an adversarial attack called \textit{FGSM} that learns to apply perturbations on a VAE's latent space vector that represents an utterance with a speaker's characterizations.
+The perturbations caused by the FGSM attack alter the latent space vector in such a way that it is as far removed from the original speaker's speech characterizations as possible, while still representing the original utterance.
+When the vector is then fed to the VAE's decoder, the decoder is unable to extract features from the perturbed vector that relate to the original speaker's speech characterizations.
+The resulting decoded speech sample is untraceable to the original speaker and thus anonymous.
 
@@
 
-We will focus on two types of adversarial attacks: \textit{Evasion Attacks} and \textit{Backdoor Attacks}.
+For the purposes of this paper, we will limit out attention to two types of adversarial attacks: \textit{Evasion Attacks} and \textit{Backdoor Attacks}.
 
@@
 This behavior should fulfill the attacker's goals.
+
+\citet{goodfellow2015explaining} introduced FGSM, the \textit{Fast Gradient Sign Method}.
+FGSM perturbs an input by exploiting a trained model's gradients.
+When given the input $x$ and its label $y$, an FGSM attack calculates the gradient with respect to the input using the model's parameters $\theta$ and loss function $J_\theta(x, y)$.
+The sign of this gradient is calculated and is added on top of the original input by a factor of $\epsilon$.
+The FGSM attack can then be defined as such:
+\begin{align*}
+  x_t &= x + \epsilon \cdot \text{sign}(\nabla_x J_\theta(x, y))
+\end{align*}
+where $x_t$ is the perturbed input.
+A visualization of this process can be found in figure \ref{fig:fgsm}.
 
@@
 
-\citet{goodfellow2015explaining} introduced FGSM, the \textit{Fast Gradient Sign Method}.
-FGSM perturbs the input by exploiting a trained model's gradients.
-When given the input $x$ and its label $y$, an FGSM attack calculates the gradient with respect to the input using the model's parameters $\theta$ and loss function $J(\theta, x, y)$.
-The sign of this gradient is calculated and is added on top of the original input by a factor of $\epsilon$.
-The FGSM attack can then be defined as such:
-\begin{align*}
-  x_t &= x + \epsilon \cdot \text{sign}(\nabla_x J(\theta, x, y))
-\end{align*}
-where $x_t$ is the perturbed input.
-A visualization of this process can be found in figure \ref{fig:fgsm}.
-
 FGSM attacks have some limitations.
-One of these limitations is that an FGSM attack is a one-step approach: the gradient with respect to the input is calculated once, and is then used immediately with to corrective measures.
-Although this makes FGSM attacks cheap, it also makes the attack difficult to perform optimally.
+One of these limitations is that an FGSM attack is a one-step approach: the gradient with respect to the input is calculated once, and is then used without corrective measures.
+Although this makes FGSM attacks cheap to perform, it also makes the attack difficult to perform optimally.
 \citet{madry2018towards} propose an expanded version of the FGSM attack called the \textit{Projected Gradient Descent} (PGD) method.
@@
 
-PGD's projection of an FGSM attack is performed by applying a clipping function $\text{clip}()$ on the FGSM attack.
+PGD's projection of an FGSM attack is performed by applying a clipping function $\text{clip}(\cdot)$ on the FGSM attack.
 The clipping function will clip gradients outside the limit of $x + S$, where $x$ is the original input data and $S$ is the predefined maximal Euclidean distance a perturbation is allowed to be from $x$.
-Prior to clipping the FGSM perturbed input $x_t$, PGD will apply another FGSM attack on the model, but will now calculate the gradient with respect to the perturbed input $x_t$ instead of the original input $x$.
+Prior to clipping the FGSM perturbed input $x_t$, PGD will fire another FGSM attack on the model, but will now calculate the gradient with respect to the perturbed input $x_t$ instead of the original input $x$.
 This additional FGSM attack is added onto $x_t$ by a factor of hyperparameter $\alpha$.
@@
 \begin{align*}
-  x_t &= x + \epsilon \cdot \text{sign}(\nabla_x J(\theta, x, y)) \\
-  x_{t+1} &= \text{clip}_{x + S}(x_t + \alpha \cdot \text{sign}(\nabla_x J(\theta, x_t, y)))
+  x_t &= x + \epsilon \cdot \text{sign}(\nabla_x J_\theta(x, y)) \\
+  x_{t+1} &= \text{clip}_{x + S}(x_t + \alpha \cdot \text{sign}(\nabla_x J_\theta(x_t, y)))
 \end{align*}
@@
 
+A well-known example of a backdoor attack is the BadNet attack by \citet{gu2019badnets}.
+BadNet attacks poison a dataset of images by adding a visual feature onto the image, such as a colored square.
+A Convolutional Neural Network (CNN) will then learn to associate the visual feature with certain behavior.
+If the model has successfully learned to associate the trigger with certain behavior, then it will display that behavior during inference when given an image with the trigger.
+The trigger may cause the model to misclassify an image, for example.
+Such an example is showcased in figure \ref{fig:badnet}.
+
 \begin{figure*}[h]
@@
 
-A well-known example of a backdoor attack is the BadNet attack by \citet{gu2019badnets}.
-BadNet attacks poison a dataset of images by adding a visual feature onto the image, such as a colored square.
-A Convolutional Neural Network (CNN) will then learn to associate the visual feature with certain behavior.
-If the model has successfully learned to associate the trigger with certain behavior, then it will display that behavior during inference when given an image with the trigger, such as misclassifying an image.
-
-Since backdoor attacks are applied during training, certain attacks can only be used on certain types of data and networks.
+Since backdoor attacks are applied during model training, certain attacks can only be used on certain types of data and networks.
 Although backdoor attacks are most often used on image data, there also exist backdoor attacks on audio data.
@@
 
+% Praat hier over de pipeline en wat het algemene idee is van je experiment.
+
 \section{Experiment}
+% Praat hier over de specifieke aanvallen die je wil doen en de metrics die je gebruikt
+% Verwijs hier naar je code
 

### 2024-05-27 paper/paper.tex
Finished related work for backdoor attacks

@@
 \subsubsection{Backdoor Attacks}
+\begin{figure*}[h]
+  \centering
+  \includegraphics[width=0.9\textwidth]{badnet.png}
+  \caption{An example of a BadNet attack \citep{gu2019badnets}.
+On the left, an image of a stop sign with varying BadNet backdoors can be seen.
+On the right, a backdoored network can be seen interpreting a stop sign as a speed limit sign due to the physical backdoor on the sign itself.}
+  \label{fig:badnet}
+\end{figure*}
+
 Backdoor attacks are adversarial attacks that are used during model training.
@@
 
-\begin{figure*}[h]
-  \centering
-  \includegraphics[width=0.9\textwidth]{badnet.png}
-  \caption{An example of a BadNet attack \citep{gu2019badnets}.
-On the left, an image of a stop sign with varying BadNet backdoors can be seen.
-On the right, a backdoored network can be seen interpreting a stop sign as a speed limit sign due to the physical backdoor on the sign itself.}
-  \label{fig:badnet}
-\end{figure*}
+Since backdoor attacks are applied during model training, certain attacks can only be used on certain types of data and networks.
+Although backdoor attacks are most common for image data and CNNs, there also exist backdoor attacks on audio data.
+\citet{liu2018trojaning} showcase a variety of backdoor attacks, including a backdoor for ASR models where the trigger is background noise that is introduced to audio.
+The ASR model is trained to associate the background noise with a specific word.
+\citet{stefanos2022ultrasonic} propose a backdoor attack on ASR systems where the trigger is inaudible.
+The trigger is a frequency that exceeds the frequency range that can be heard by a human, which should make the trigger impossible to detect by the human ear.
 
-Since backdoor attacks are applied during model training, certain attacks can only be used on certain types of data and networks.
-Although backdoor attacks are most often used on image data, there also exist backdoor attacks on audio data.
-\dots % Ga hier door!
-\citet{liu2018trojaning} % The paper about trojanning audio. Keep it brief. Use it to show that backdooring audio is also possible.
-\citet{stefanos2022ultrasonic} % The paper about ultrasonic frequencies for backdooring. Keep it brief. Another example of audio backdoor.
-
-% Nieuwe alinea
-\citet{stefanos2023jingleback} % Jingleback paper. Explain in more details since you will focus on it.
+In \citet{stefanos2023jingleback}, the authors propose a backdoor based on stylistic triggers called \textit{JingleBack}.
+The trigger in a JingleBack attack is a digital music effect applied on the audio, such as a pitch shift or reverb.
+A neural ASR model learns to associate certain combinations of effects with certain behavior.
+In their work, \citeauthor{stefanos2023jingleback} backdoor neural models of three different architectures (small CNN, large CNN, and LSTM) using six different combinations of digital effects.
+They find that certain combinations of effects are more effective triggers than others, and that additional effects do not necessarily improve the trigger's effectiveness.
+The most effective trigger found by the authors was to increase the audio's amplitude by 12dB, then apply a high-pass ladder filter, and then apply a phaser filter.
+This trigger results in a rate of attack success of up to nearly 95\% when only 0.5\% of the training data is poisoned.
 
 \subsection{Attacks on Neural Speech Systems}
+\citet{chen2022survey} % Survery about adversarial attacks on ASR models
+
 \citet{neekhara2019universal} % Paper about adversarial attacks on ASR systems

### 2024-05-27 paper/paper.tex
Finished related works section (for now)

@@
 
-\subsection{Attacks on Neural Networks}
+\subsection{Adversarial Attacks on Neural Networks}
 The FGSM attack used by \citet{shihao2024adversarial} is an example of an adversarial attack.
@@
 They provide an introduction to and an overview of adversarial attacks within the deep learning domain, and should provide the reader with plentiful knowledge on the topic.
+\citet{chen2022survey} provide an overview of adversarial attacks aimed at speech systems, including ASR systems.
 
@@
 
-\subsection{Attacks on Neural Speech Systems}
-\citet{chen2022survey} % Survery about adversarial attacks on ASR models
+%%%%% Low priority, not needed for understanding the project, so only write if there's time left.
+% \subsection{Adversarial Attacks on Neural Speech Systems}
+% As demonstrated by \citet{liu2018trojaning,stefanos2022ultrasonic,stefanos2023jingleback}, neural ASR systems are shown to be susceptible to backdoor attacks.
+% The range of adversarial attacks aimed at neural speech systems is not limited backdoor attacks, however.
 
-\citet{neekhara2019universal} % Paper about adversarial attacks on ASR systems
-
-\citet{kreuk2018fooling} % Paper about adversarial attacks on E2E speaker verification
+% \citet{carlini2018audio}
+% \citet{alzantot2018didyouhearthat}
+% \citet{carlini2016hiddenvc}
+% \citet{iter2017generating}
+% \citet{vaidya2015cocainenoodles}
+% \citet{neekhara2019universal}
+% \citet{kreuk2018fooling}
 

### 2024-05-27 paper/paper.tex
Wrote about related work for Method section

@@
 
-\title{(Automatic) Speech Recognition Project --- Attacks on Neural Networks in a Lightweight Speech Anonymization Pipeline}
+\title{(Automatic) Speech Recognition Project --- Attacks on Neural Networks in a Lightweight Speech Pseudonymization Pipeline}
 
@@
 The resulting decoded speech sample is untraceable to the original speaker and thus anonymous.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.45\textwidth]{kai_etal_pipeline.png}
+  \caption{The lightweight pseudonymization pipeline by \citet{kai2022lightweight} visualized.}
+  \label{fig:kai_etal_pipeline}
+\end{figure}
+
+\citet{kai2022lightweight} showcase a lightweight Speaker Anonymization pipeline.
+Their proposed pipeline pseudonymizes speech by applying voice modifications to the spoken utterances.
+In their pipeline, the authors make use of a neural ASR model alongside an \textit{Automatic Speaker Verification} (ASV) model, which are used for the recognition of words and speakers respectively.
+Instead of optimizing the performance of the ASR and ASV model, the authors attempt to optimize the voice modifications applied to the utterances.
+The optimization is performed by minimizing the \textit{Word Error Rate} (WER) and maximizing the \textit{Equal Error Rate} (EER).
+Figure \ref{fig:kai_etal_pipeline} shows the design of the proposed pipeline.
+
+By refraining from using neural models to anonymize the speech itself, and instead opting to use existing neural models only for evaluation purposes, the pseudonymization of the utterances becomes a relatively cheap operation.
+However, although the method proposed by \citeauthor{kai2022lightweight} is lightweight during inference, it does require that an optimal parameter set for the speech modifications is found first, which is a more resource intensive process.
+It should also be noted that this process produces pseudonymized speech, and not anonymous speech; the original speaker could potentially be recognizable, even if only slightly.
+
+\citet{roddeman2024anonymization} expand upon the work by \citet{kai2022lightweight} by proposing their own lightweight speaker pseudonymization optimization pipeline.
+The authors' aims are to produce a pseudonymization pipeline that is resource efficient, easy to deploy, and optimizes swiftly.
+Their pipeline uses the same optimization strategy used by \citeauthor{kai2022lightweight}: pre-trained ASR and ASV models are used to calculate the WER and EER, which are used to optimize a set of audio modifications for pseudonymization purposes.
+
+The authors performed 300 optimization trials, and evaluated their results on samples of utterances spoken by both men and women.
+They found that the most effective modifications for pseudonymization purposes include a time stretch factor, an increase in dB, and applying a low-pass cutoff.
+However, they also found that the effectiveness of a modification varies by the speaker's gender: while a time stretch factor was effective for both male and female spoken utterances, low-pass cutoffs only seemed effective on female-spoken utterances.
+\citeauthor{roddeman2024anonymization}'s implementation uses Pedalboard \citep{sobot2021pedalboard} for applying the audio modifications and Optuna \citep{akiba2019optuna} for the optimization process.
 
@@
 In their work, \citeauthor{stefanos2023jingleback} backdoor neural models of three different architectures (small CNN, large CNN, and LSTM) using six different combinations of digital effects.
+These effects were applied using Pedalboard \citep{sobot2021pedalboard}.
 They find that certain combinations of effects are more effective triggers than others, and that additional effects do not necessarily improve the trigger's effectiveness.
@@
 \section{Method}
-\citet{kai2022lightweight} % Work on lightweight speaker anonymization, idea for our method/pipeline.
-
 % Praat hier over de pipeline en wat het algemene idee is van je experiment.

### 2024-05-27 paper/paper.tex
Finished method section

@@
 \usepackage{amsmath}
+\usepackage{csquotes}
 
@@
 
+For this paper, we attempt to answer the following Research Question:
+\begin{displayquote}
+  \textit{How (effectively) can we manipulate a Speaker Anonymization pipeline by adversarially attacking its neural speech systems?}
+\end{displayquote}
+
 \section{Related Work}
@@
 
-\citet{roddeman2024anonymization} expand upon the work by \citet{kai2022lightweight} by proposing their own lightweight speaker pseudonymization optimization pipeline.
+\citet{roddeman2024anonymization} expand upon the work by \citet{kai2022lightweight} by proposing their own lightweight speaker pseudonymization optimization pipeline, shown in figure \ref{fig:roddeman_etal_optimization}.
 The authors' aims are to produce a pseudonymization pipeline that is resource efficient, easy to deploy, and optimizes swiftly.
 Their pipeline uses the same optimization strategy used by \citeauthor{kai2022lightweight}: pre-trained ASR and ASV models are used to calculate the WER and EER, which are used to optimize a set of audio modifications for pseudonymization purposes.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.9\textwidth]{roddeman_etal_optimization.png}
+  \caption{The optimization process of the lightweight pseudonymization pipeline by \citet{roddeman2024anonymization}.}
+  \label{fig:roddeman_etal_optimization}
+\end{figure*}
 
@@
 \section{Method}
-% Praat hier over de pipeline en wat het algemene idee is van je experiment.
+From the perspective of an adversarial attacker, \citet{roddeman2024anonymization}'s pseudonymization pipeline has at least two noticeable points of attack:
+\begin{enumerate}
+  \item The authors use neural ASR and ASV networks to evaluate the pseudonymization strategy. 
+  Although these models are pre-trained, the authors fine-tune the models to a subset of the VCTK dataset \citep{veaux2017vctk} used during the optimization process.
+  Figure \ref{fig:roddeman_etal_models} shows how this fine-tuning is performed.
+  Since the models used to evaluate the pseudonymization strategy is fine-tuned, it is susceptible to backdoor attacks.
+  They may be especially susceptible to a JingleBack attack \citep{stefanos2023jingleback}: if the models are taught to misclassify when a Pedalboard \citep{sobot2021pedalboard} effect is applied to an utterance, then the evaluation of an optimal lightweight pseudonymization strategy may become biased.
+  \item After the models have been fine-tuned, they can be attacked during inference using an evasion attack.
+  Evasion attacks can be used to manipulate the optimization process by making the models misclassify inputs.
+\end{enumerate}
+
+We will test the effect of evasion and backdoor attacks on the pipeline by \citeauthor{roddeman2024anonymization} and to what extent the optimization strategy employed by their pipeline can be exploited.
+We will attempt to poison the fine-tuning dataset of the ASR and ASV models by inserting a backdoor from Pedalboard.
+This backdoor should be an effect that is not already used by \citeauthor{roddeman2024anonymization}.
+They use the following effects in their optimization pipeline:
+\begin{itemize}
+  \item High-pass Filter
+  \item Low-pass Filter
+  \item Time Stretch
+  \item Pitch Shift
+  \item Distortion
+  \item Bitcrush
+  \item Phaser
+  \item Gain in dB
+\end{itemize}
+Notably, this does not include the use of a Ladder Filter, which is employed by \citet{stefanos2023jingleback} in their most effective JingleBack attack.
+We will follow their example and attempt to insert a backdoor into the ASR and ASV models using the Ladder Filter effect as the trigger.
+After fine-tuning, the models will then receive speech utterances with the Ladder Filter effect applied, and should then misclassify the input to a set target class.
+We will also attack the clean versions of the ASR and ASV models during inference.
+We will do this by perturbing utterances using both FGSM and PGD.
+
+We will assess the success of the attacks using varying measures.
+The \textit{Attack Success Rate} (ASR) measures the rate that an attack has successfully led to the desired misclassification.
+The Attack Success Rate is the number of utterances not in the target class that are misclassified as being in the target class, divided by the number of utterances not in the target class.
+For backdoor attacks, we also normally calculate the \textit{Clean Accuracy Drop} (CAD), which is the amount of percentage points the accuracy of the clean model has decreased after it was backdoored.
+However, the performance of the ASR model is not measured using accuracy, but with WER.
+That is why we will measure the decrease in performance for the ASR model using the \textit{Word Error Rate Increase} (WERI).
+The ASV model's performance is assessed using the accuracy metric, so we can use the CAD to measure the decrease in its performance after poisoning the data.
+For reference, the WER of the ASR model and the accuracy of the ASV model are also calculated.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{roddeman_etal_models.png}
+  \caption{Fine-tuning of the neural ASR and ASV models in \citet{roddeman2024anonymization}.}
+  \label{fig:roddeman_etal_models}
+\end{figure}
 
 \section{Experiment}
-% Praat hier over de specifieke aanvallen die je wil doen en de metrics die je gebruikt
-% Verwijs hier naar je code
+% Specify the specific settings and individual attacks you performed.
+  % Backdoor attack (JingleBack): poisoning rate, ...
+  % Evasion attack (FGSM and PGD): ...
+
+% Specify the transliteration and speaker you want the models to pick when they get the backdoor.
+
+The code used for the experiments performed can be found at the following URL: \url{https://github.com/daanbrugmans/ru-automatic-speech-recognition-23-24}
 

### 2024-06-02 code/attacks/abstract_backdoor_attack.py
Added basic code for experiments

@@ -1,0 +1,15 @@
+from abc import ABC, abstractmethod
+
+import torch
+
+
+class AbstractBackdoorAttack(ABC):
+    def __init__(self) -> None:
+        self.attack_name: str
+        
+        self.source_label: int
+        self.target_label: int
+    
+    @abstractmethod
+    def execute(self, image: torch.Tensor):
+        raise NotImplementedError("The BackdoorAttack base class is abstract. Please use an implementation of an Attack.")

### 2024-06-02 code/attacks/jingleback.py

@@ -1,0 +1,14 @@
+from attacks.abstract_backdoor_attack import AbstractBackdoorAttack
+
+import pedalboard
+import torch
+
+class Jingleback(AbstractBackdoorAttack):
+    def __init__(self, source_label = int, target_label = int) -> None:
+        self.attack_name = "Jingleback Attack"
+        
+        self.source_label = source_label
+        self.target_label = target_label
+    
+    def execute(self, audio: torch.Tensor):
+        pass

### 2024-06-02 code/backdoored_dataset.py

@@ -1,0 +1,91 @@
+from attacks.abstract_backdoor_attack import AbstractBackdoorAttack
+
+import torch
+from torch.utils.data import Dataset
+from torch.utils.data import DataLoader
+from torch.utils.data import random_split
+
+class BackdooredDataset(Dataset):
+        def __init__(self, backdoor: AbstractBackdoorAttack, train: bool) -> None:
+            super().__init__()
+            
+            self.epsilon = 0.08
+                        
+            self.clean_dataset = ...
+            self.clean_dataloader = DataLoader(self.clean_dataset, batch_size=1, shuffle=True)
+            
+            self.backdoor = backdoor
+            self.backdoored_dataset = []
+            self.backdoored_sample_count = round(len(self.clean_cifar10) * self.epsilon, 0)
+                        
+            if train:
+                self._backdoor_train()
+            else:
+                self._backdoor_test()
+                                                                
+        def __len__(self) -> int:
+            return len(self.backdoored_dataset)
+        
+        def __getitem__(self, index):
+            return self.backdoored_dataset[index]
+        
+        def _backdoor_train(self):
+            # If attack is source agnostic
+            if self.backdoor.source_label is None:
+                for index, (image, label) in enumerate(self.clean_cifar10_loader):
+                    label = label.item()
+                    image = torch.squeeze(image, 0)
+                    
+                    # If the utterance belongs to the subset of audio we want to backdoor
+                    if index < self.backdoored_sample_count:
+                        backdoored_image = self.backdoor.execute(image)
+                        self.backdoored_cifar10.append((backdoored_image, self.backdoor.target_label))
+                    # If the utterance does not belong to the subset of audio we want to backdoor
+                    else:
+                        self.backdoored_cifar10.append((image, label))
+                    
+            # If attack is source specific
+            else:
+                for index, (image, label) in enumerate(self.clean_cifar10_loader):
+                    label = label.item()
+                    image = torch.squeeze(image, 0)
+                
+                    # If the utterance belongs to the subset of audio we want to backdoor
+                    if index < self.backdoored_sample_count:
+                        backdoored_image = self.backdoor.execute(image)
+                    
+                        if label == self.backdoor.source_label:
+                            self.backdoored_cifar10.append((backdoored_image, self.backdoor.target_label))
+                        else:
[…]

### 2024-06-02 code/metrics.py

@@ -1,0 +1,156 @@
+from neural_model import NeuralModel
+
+from copy import copy
+
+from tqdm import tqdm
+
+import torch
+from torch.utils.data import DataLoader
+
+def _count_non_source_misclassifications(targets: torch.Tensor, predictions: torch.Tensor, source_label, target_label):
+    """Calculates and returns the number of classifications of images with a label that is not the source label nor the target label.
+    
+    Taken from the Security & Privacy of Machine Learning course (dr. Picek) and refactored."""
+    
+    sub_non_source_total = 0
+    sub_misclassifications = 0
+    
+    sub_non_source_total_dict = {}
+    sub_misclassification_dict = {}
+
+    # Find all the images with a different label than the source or target label
+    indices = torch.logical_and((targets != source_label), (targets != target_label)).nonzero(as_tuple=False).numpy()
+    indices = indices.reshape(indices.shape[0])
+    sub_non_source_total += indices.shape[0]
+
+    # For all non-source and non-target label images, check if the prediction is equal to the target label
+    for index in indices:
+        target = targets[index].detach().cpu().numpy()
+        prediction = predictions[index].detach().cpu().numpy()
+        
+        if str(target) in sub_non_source_total_dict:
+            sub_non_source_total_dict[str(target)] += 1
+        else:
+            sub_non_source_total_dict[str(target)] = 1
+        
+        if prediction == target_label:
+            sub_misclassifications += 1
+            
+            if str(target) in sub_misclassification_dict:
+                sub_misclassification_dict[str(target)] += 1
+            else:
+                sub_misclassification_dict[str(target)] = 1
+    
+    return sub_misclassifications, sub_non_source_total, sub_misclassification_dict, sub_non_source_total_dict
+
+def _count_source_specific_classifications(targets: torch.Tensor, predictions: torch.Tensor, source_label: int, target_label: int):
+    """Calculates and returns the number of classifications of images with the source label.
+    
+    Taken from the Security & Privacy of Machine Learning course (dr. Picek) and refactored."""
+    sub_total = 0
+    sub_correct = 0
+    
+    # Find all the images with the source label
+    indices = (targets == source_label).nonzero(as_tuple=False).numpy()
+    indices = indices.reshape(indices.shape[0])
+    sub_total += indices.shape[0]
+    
+    # For all source label images, check if the prediction is equal to the target label
+    for i in indices:
+        if predictions[i].detach().cpu().numpy() == target_label:
+            sub_correct += 1
+    
+    return sub_correct, sub_total
+
[…]

### 2024-06-02 code/neural_model.py

@@ -1,0 +1,174 @@
+from attacks.abstract_backdoor_attack import AbstractBackdoorAttack
+from backdoored_dataset import get_dataloaders
+
+import matplotlib.pyplot as plt
+import numpy as np
+import sklearn
+from tqdm import tqdm
+
+import torch
+from torch import nn
+
+class NeuralModel:
+    def __init__(self, device, epochs: int = 30, attack: AbstractBackdoorAttack = None) -> None:
+        self.neural_network = ....to(device)
+        self.loss_function = ...
+        self.optimizer = torch.optim.AdamW(self.neural_network.parameters(), lr=0.001)
+        self.epochs = epochs
+        self.device = device
+        
+        if attack is None:
+            self.train_data, self.val_data, self.test_data = get_dataloaders()
+            self.attack = None
+        else:
+            self.train_data, self.val_data, self.test_data = get_dataloaders(backdoor=attack)
+            self.attack = attack
+        
+        self.history = None
+        
+    def train(self):
+        """Train the network."""
+        
+        # Keep record of loss and accuracy metrics for most recent training procedure
+        self.history = {
+            "Train Type": "Clean" if self.attack is None else f"Adversarial ({self.attack.attack_name})",
+            "Train Loss": [],
+            "Validation Loss": [],
+            "Train Accuracy": [],
+            "Validation Accuracy": []
+        }
+        
+        for epoch in range(self.epochs):
+            print(f"Started Epoch {epoch + 1}")
+            
+            self.neural_network.train()
+            
+            # Train
+            print(" Training...")
+            
+            train_batch_losses = []
+            train_batch_accuracies = []
+            
+            for images, targets in tqdm(self.train_data):
+                images = images.to(self.device)
+                targets = targets.to(self.device)
+                
+                predictions = self.neural_network(images)
+                
+                # Calculate train loss and backpropagate
+                train_batch_loss = self.loss_function(predictions, targets)
+                train_batch_losses.append(train_batch_loss)
+                train_batch_loss.backward()
+                
+                # Move predictions and labels to cpu for accuracy calculation
+                predictions = torch.max(predictions, dim=1)[1]
+                predictions = predictions.cpu().detach().numpy()
+                targets = targets.cpu().detach().numpy()
+                
+                # Calculate train accuracy
+                train_batch_accuracy = sklearn.metrics.accuracy_score(y_pred=predictions, y_true=targets)
+                train_batch_accuracies.append(train_batch_accuracy)
+                
[…]

### 2024-06-02 code/util.py

@@ -1,0 +1,17 @@
+import random
+
+import numpy as np
+import torch
+
+def set_global_seed(seed):
+    """Sets the same seed for varying libraries."""
+    torch.manual_seed(seed)
+    np.random.seed(seed)
+    random.seed(seed)
+
+    if torch.cuda.is_available():
+        torch.cuda.manual_seed(seed)
+        torch.cuda.manual_seed_all(seed)
+
+        torch.backends.cudnn.benchmark = False
+        torch.backends.cudnn.deterministic = True

### 2024-06-02 paper/paper.tex
Found correct code for setting targeted evasion attack

@@
 
-The code used for the experiments performed can be found at the following URL: \url{https://github.com/daanbrugmans/ru-automatic-speech-recognition-23-24}
+The code used for the experiments performed can be found at the following URL: \url{https://github.com/daanbrugmans/ru-automatic-speech-recognition-23-24}.
+
+\citet{kim2020torchattacks}
 

### 2024-06-03 paper/paper.tex
WIP Updated BackdooredDataset functionality

@@
   \item The authors use neural ASR and ASV networks to evaluate the pseudonymization strategy. 
-  Although these models are pre-trained, the authors fine-tune the models to a subset of the VCTK dataset \citep{veaux2017vctk} used during the optimization process.
+  Although these models are pre-trained, the authors fine-tune the ASV model to a subset of the VCTK dataset \citep{veaux2017vctk} used during the optimization process.
   Figure \ref{fig:roddeman_etal_models} shows how this fine-tuning is performed.
-  Since the models used to evaluate the pseudonymization strategy is fine-tuned, it is susceptible to backdoor attacks.
-  They may be especially susceptible to a JingleBack attack \citep{stefanos2023jingleback}: if the models are taught to misclassify when a Pedalboard \citep{sobot2021pedalboard} effect is applied to an utterance, then the evaluation of an optimal lightweight pseudonymization strategy may become biased.
-  \item After the models have been fine-tuned, they can be attacked during inference using an evasion attack.
-  Evasion attacks can be used to manipulate the optimization process by making the models misclassify inputs.
+  Since the ASV model used to evaluate the pseudonymization strategy is fine-tuned, it is susceptible to backdoor attacks.
+  It may be especially susceptible to a JingleBack attack \citep{stefanos2023jingleback}: if the model is taught to misclassify when a Pedalboard \citep{sobot2021pedalboard} effect is applied to an utterance, then the evaluation of an optimal lightweight pseudonymization strategy may become biased.
+  \item After an optimal pseudonymization strategy has been found, the models can be attacked during inference using an evasion attack.
+  Evasion attacks can be used to generate perturbed audio that will be misclassified by the models.
 \end{enumerate}
@@
 We will test the effect of evasion and backdoor attacks on the pipeline by \citeauthor{roddeman2024anonymization} and to what extent the optimization strategy employed by their pipeline can be exploited.
-We will attempt to poison the fine-tuning dataset of the ASR and ASV models by inserting a backdoor from Pedalboard.
+We will attempt to poison the fine-tuning dataset of the ASV model by inserting a backdoor from Pedalboard.
 This backdoor should be an effect that is not already used by \citeauthor{roddeman2024anonymization}.
@@
 Notably, this does not include the use of a Ladder Filter, which is employed by \citet{stefanos2023jingleback} in their most effective JingleBack attack.
-We will follow their example and attempt to insert a backdoor into the ASR and ASV models using the Ladder Filter effect as the trigger.
-After fine-tuning, the models will then receive speech utterances with the Ladder Filter effect applied, and should then misclassify the input to a set target class.
+We will follow their example and attempt to insert a backdoor into the ASV model using the Ladder Filter effect as the trigger.
+After fine-tuning, the model will then receive speech utterances with the Ladder Filter effect applied, and should then misclassify the input to a set target class.
 We will also attack the clean versions of the ASR and ASV models during inference.
@@
 The Attack Success Rate is the number of utterances not in the target class that are misclassified as being in the target class, divided by the number of utterances not in the target class.
-For backdoor attacks, we also normally calculate the \textit{Clean Accuracy Drop} (CAD), which is the amount of percentage points the accuracy of the clean model has decreased after it was backdoored.
-However, the performance of the ASR model is not measured using accuracy, but with WER.
-That is why we will measure the decrease in performance for the ASR model using the \textit{Word Error Rate Increase} (WERI).
+For backdoor attacks, we also usually calculate the \textit{Clean Accuracy Drop} (CAD), which is the amount of percentage points the accuracy of the clean model has decreased after it was backdoored.
+% However, the performance of the ASR model is not measured using accuracy, but with WER.
+% That is why we will measure the decrease in performance for the ASR model using the \textit{Clean Word Error Rate Increase} (CWERI).
 The ASV model's performance is assessed using the accuracy metric, so we can use the CAD to measure the decrease in its performance after poisoning the data.

### 2024-06-03 code/ASR_2024_anonymization_module_learning/main.py

@@ -1,7 +1,7 @@
 from multiprocessing import Pool, cpu_count
 
-from speaker_anonymization.config import Config
-from speaker_anonymization.optimize import optimize_audio_effects
+from ASR_2024_anonymization_module_learning.speaker_anonymization.config import Config
+from ASR_2024_anonymization_module_learning.speaker_anonymization.optimize import optimize_audio_effects
 
 
 def run_optimization(config):

### 2024-06-03 code/ASR_2024_anonymization_module_learning/speaker_anonymization/asr.py

@@ -3,9 +3,9 @@ import logging
 import torch
 from transformers import Wav2Vec2ForCTC, Wav2Vec2Processor
 
-from speaker_anonymization.data import get_audio_data_wavs
-from speaker_anonymization.losses import average_wer, normalized_wer
-from speaker_anonymization.utils import load_audio
+from ASR_2024_anonymization_module_learning.speaker_anonymization.data import get_audio_data_wavs
+from ASR_2024_anonymization_module_learning.speaker_anonymization.losses import average_wer, normalized_wer
+from ASR_2024_anonymization_module_learning.speaker_anonymization.utils import load_audio
 
 logging.basicConfig(
     level=logging.INFO, format="%(asctime)s - %(levelname)s - %(message)s"

### 2024-06-03 code/ASR_2024_anonymization_module_learning/speaker_anonymization/optimize.py

@@ -16,15 +16,15 @@ from pedalboard import (
     time_stretch,
 )
 
-from speaker_anonymization.asr import (
+from ASR_2024_anonymization_module_learning.speaker_anonymization.asr import (
     load_audio,
     load_pretrained_model,
     transcribe_audio,
 )
-from speaker_anonymization.data import get_audio_data_wavs
-from speaker_anonymization.losses import calculate_combined_loss
-from speaker_anonymization.spi import SpeakerIdentificationModel
-from speaker_anonymization.utils import save_audio_file, save_optimization_plots
+from ASR_2024_anonymization_module_learning.speaker_anonymization.data import get_audio_data_wavs
+from ASR_2024_anonymization_module_learning.speaker_anonymization.losses import calculate_combined_loss
+from ASR_2024_anonymization_module_learning.speaker_anonymization.spi import SpeakerIdentificationModel
+from ASR_2024_anonymization_module_learning.speaker_anonymization.utils import save_audio_file, save_optimization_plots
 
 
 def optimize_audio_effects(CONFIG):

### 2024-06-03 code/ASR_2024_anonymization_module_learning/speaker_anonymization/spi.py

@@ -8,10 +8,10 @@ from torch import nn
 from tqdm import tqdm
 from transformers import Wav2Vec2Model, Wav2Vec2Processor
 
-from speaker_anonymization.config import Config
-from speaker_anonymization.data import get_audio_data_wavs
-from speaker_anonymization.losses import speaker_verification_loss
-from speaker_anonymization.utils import load_audio
+from ASR_2024_anonymization_module_learning.speaker_anonymization.config import Config
+from ASR_2024_anonymization_module_learning.speaker_anonymization.data import get_audio_data_wavs
+from ASR_2024_anonymization_module_learning.speaker_anonymization.losses import speaker_verification_loss
+from ASR_2024_anonymization_module_learning.speaker_anonymization.utils import load_audio
 
 if torch.backends.mps.is_available() and torch.backends.mps.is_built():
     device = torch.device("mps")
@@ -43,19 +43,20 @@ class SpeakerIdentificationModel:
         logits = self.classifier(embeddings)
         return logits
 
-    def finetune_model(self, speaker_labels, files, n_epochs=10, learning_rate=1e-2):
-        try:
-            cached_model = torch.load(
-                f"code/ASR-2024-anonymization-module-learning/checkpoints/{self.study_name}/speaker_verification_model_{self.num_speakers}_{n_epochs}_{learning_rate}.pt"
-            )
-        except FileNotFoundError:
-            cached_model = None
-        if cached_model:
-            self.classifier.load_state_dict(cached_model)
-            print(
-                f"Loaded cached model for {self.num_speakers} speakers and {n_epochs} epochs."
-            )
-            return
+    def finetune_model(self, speaker_labels, files, n_epochs=10, learning_rate=1e-2, try_cached_model: bool = True):
+        if try_cached_model:
+            try:
+                cached_model = torch.load(
+                    f"d:/Models/ASR_2024_anonymization_module_learning/{self.study_name}/speaker_verification_model_{self.num_speakers}_{n_epochs}_{learning_rate}.pt"
+                )
+            except FileNotFoundError:
+                cached_model = None
+            if cached_model:
+                self.classifier.load_state_dict(cached_model)
+                print(
+                    f"Loaded cached model for {self.num_speakers} speakers and {n_epochs} epochs."
+                )
+                return
         self.model.train()
         optimizer = torch.optim.Adam(self.classifier.parameters(), lr=learning_rate)
[…]

### 2024-06-03 code/attacks/backdoor_attack.py

@@ -3,7 +3,7 @@ from abc import ABC, abstractmethod
 import torch
 
 
-class AbstractBackdoorAttack(ABC):
+class BackdoorAttack(ABC):
     def __init__(self) -> None:
         self.attack_name: str
         

### 2024-06-03 code/attacks/jingleback.py

@@ -1,9 +1,9 @@
-from attacks.abstract_backdoor_attack import AbstractBackdoorAttack
+from attacks.backdoor_attack import BackdoorAttack
 
 import pedalboard
 import torch
 
-class Jingleback(AbstractBackdoorAttack):
+class JingleBack(BackdoorAttack):
     def __init__(self, source_label = int, target_label = int) -> None:
         self.attack_name = "Jingleback Attack"
         

### 2024-06-03 code/backdoored_dataset.py

@@ -1,22 +1,28 @@
-from attacks.abstract_backdoor_attack import AbstractBackdoorAttack
+import ASR_2024_anonymization_module_learning.speaker_anonymization.data
+import ASR_2024_anonymization_module_learning.speaker_anonymization.utils
+from ASR_2024_anonymization_module_learning.speaker_anonymization.config import Config
 
-import torch
+from attacks.backdoor_attack import BackdoorAttack
+
+import datasets.load
+
 from torch.utils.data import Dataset
 from torch.utils.data import DataLoader
 from torch.utils.data import random_split
 
-class BackdooredDataset(Dataset):
-        def __init__(self, backdoor: AbstractBackdoorAttack, train: bool) -> None:
+class BackdooredVCTK(Dataset):
+        def __init__(self, backdoor: BackdoorAttack, epsilon: float, train: bool, pipeline_config: Config) -> None:
             super().__init__()
             
-            self.epsilon = 0.08
+            self.epsilon = epsilon
                         
-            self.clean_dataset = ...
+            # self.clean_dataset = datasets.load.load_dataset("vctk", split="train" if train else "test", cache_dir="d:/Datasets/vctk/cache")
+            self.clean_dataset = CachedVCTK(pipeline_config)
             self.clean_dataloader = DataLoader(self.clean_dataset, batch_size=1, shuffle=True)
             
             self.backdoor = backdoor
             self.backdoored_dataset = []
-            self.backdoored_sample_count = round(len(self.clean_cifar10) * self.epsilon, 0)
+            self.backdoored_sample_count = round(len(self.clean_dataset) * self.epsilon, 0)
                         
             if train:
                 self._backdoor_train()
@@ -32,53 +38,69 @@ class BackdooredDataset(Dataset):
         def _backdoor_train(self):
             # If attack is source agnostic
             if self.backdoor.source_label is None:
-                for index, (image, label) in enumerate(self.clean_cifar10_loader):
-                    label = label.item()
-                    image = torch.squeeze(image, 0)
+                for index, (utterance, _, speaker_id) in enumerate(self.clean_dataloader):
+                    speaker_id = speaker_id.item()
                     
                     # If the utterance belongs to the subset of audio we want to backdoor
                     if index < self.backdoored_sample_count:
-                        backdoored_image = self.backdoor.execute(image)
-                        self.backdoored_cifar10.append((backdoored_image, self.backdoor.target_label))
+                        backdoored_utterance = self.backdoor.execute(utterance)
[…]

### 2024-06-03 code/neural_model.py

@@ -1,4 +1,4 @@
-from attacks.abstract_backdoor_attack import AbstractBackdoorAttack
+from attacks.backdoor_attack import BackdoorAttack
 from backdoored_dataset import get_dataloaders
 
 import matplotlib.pyplot as plt
@@ -10,7 +10,7 @@ import torch
 from torch import nn
 
 class NeuralModel:
-    def __init__(self, device, epochs: int = 30, attack: AbstractBackdoorAttack = None) -> None:
+    def __init__(self, device, epochs: int = 30, attack: BackdoorAttack = None) -> None:
         self.neural_network = ....to(device)
         self.loss_function = ...
         self.optimizer = torch.optim.AdamW(self.neural_network.parameters(), lr=0.001)

### 2024-06-03 code/ASR_2024_anonymization_module_learning/speaker_anonymization/config.py
WIP backdooring ASV model

@@ -39,9 +39,10 @@ class Config:
     IMAGES_DIR = "code/ASR-2024-anonymization-module-learning/images"
     CACHE_FOLDER = "d:/Datasets/vctk/cache"#"cache"
     ANONYMIZED_FOLDER = "d:/Datasets/vctk/anonymized_audio"
+    BACKDOORED_FOLDER = "d:/Datasets/vctk/backdoored_audio"
     SHOW_PROGRESS_BAR = False
     CONFIG_N_JOBS = 1  # Number of jobs to run in parallel, -1 means use all
-    SEED = 42
+    SEED = 3131
 
     # ASR CONFIG
     ASR_BACKBONE = "Somebody433/fine-tuned-vctkdataset"

### 2024-06-03 code/ASR_2024_anonymization_module_learning/speaker_anonymization/optimize.py

@@ -26,155 +26,26 @@ from ASR_2024_anonymization_module_learning.speaker_anonymization.losses import 
 from ASR_2024_anonymization_module_learning.speaker_anonymization.spi import SpeakerIdentificationModel
 from ASR_2024_anonymization_module_learning.speaker_anonymization.utils import save_audio_file, save_optimization_plots
 
+from backdoored_dataset import BackdooredVCTK
 
-def optimize_audio_effects(CONFIG):
+
+def optimize_audio_effects(CONFIG, backdoored_vctk: BackdooredVCTK = None):
     logging.basicConfig(
         level=logging.INFO, format="%(asctime)s - %(levelname)s - %(message)s"
     )
 
     os.makedirs(CONFIG.IMAGES_DIR, exist_ok=True)
 
-    def apply_audio_effects(audio, sample_rate, params):
-        """
-        Apply audio effects based on pedalboard library with given parameters.
-        Convert PyTorch tensor to numpy array for compatibility with the pedalboard library.
-        """
-
-        if isinstance(audio, torch.Tensor):
-            audio = audio.numpy()
-
-        board = Pedalboard(
-            [
-                Distortion(drive_db=params["distortion_drive_db"]),
-                PitchShift(semitones=params["pitch_shift_semitones"]),
-                HighpassFilter(cutoff_frequency_hz=params["highpass_cutoff"]),
-                LowpassFilter(cutoff_frequency_hz=params["lowpass_cutoff"]),
-                Bitcrush(bit_depth=params["bitcrush_bit_depth"]),
-                Chorus(rate_hz=params["chorus_rate_hz"]),
-                Phaser(rate_hz=params["phaser_rate_hz"]),
-                Gain(gain_db=params["gain_db"]),
-            ],
-        )
-        processed_audio = board(audio, sample_rate=int(sample_rate))
-        processed_audio = time_stretch(
-            processed_audio, sample_rate, params["time_stretch_factor"]
-        )
-        return processed_audio
-
-    def evaluate_asr_and_asv(audio_data, transcriptions, speakers):
-        """Evaluate ASR and ASV models and log results using the modified audio."""
-        predictions = []
[…]

### 2024-06-03 code/attacks/backdoor_attack.py

@@ -11,5 +11,5 @@ class BackdoorAttack(ABC):
         self.target_label: int
     
     @abstractmethod
-    def execute(self, image: torch.Tensor):
+    def execute(self, utterance: torch.Tensor, sample_rate: float):
         raise NotImplementedError("The BackdoorAttack base class is abstract. Please use an implementation of an Attack.")

### 2024-06-03 code/attacks/jingleback.py

@@ -1,14 +1,22 @@
 from attacks.backdoor_attack import BackdoorAttack
 
-import pedalboard
 import torch
+from pedalboard import Pedalboard, LadderFilter, Gain, Phaser
 
 class JingleBack(BackdoorAttack):
     def __init__(self, source_label = int, target_label = int) -> None:
-        self.attack_name = "Jingleback Attack"
+        self.attack_name = "JingleBack Attack"
         
         self.source_label = source_label
         self.target_label = target_label
     
-    def execute(self, audio: torch.Tensor):
-        pass
+    def execute(self, utterance: torch.Tensor, sample_rate: float) -> torch.Tensor:
+        utterance = utterance.numpy()
+        
+        board = Pedalboard([
+            LadderFilter(mode=LadderFilter.Mode.HPF12, cutoff_hz=1000),
+        ])
+        
+        backdoored_utterance = board(utterance, sample_rate=sample_rate)
+        
+        return torch.from_numpy(backdoored_utterance)

### 2024-06-03 code/backdoored_dataset.py

@@ -4,17 +4,21 @@ from ASR_2024_anonymization_module_learning.speaker_anonymization.config import 
 
 from attacks.backdoor_attack import BackdoorAttack
 
+import os
+
 import datasets.load
 
+import torchaudio
 from torch.utils.data import Dataset
 from torch.utils.data import DataLoader
 from torch.utils.data import random_split
 
 class BackdooredVCTK(Dataset):
-        def __init__(self, backdoor: BackdoorAttack, epsilon: float, train: bool, pipeline_config: Config) -> None:
+        def __init__(self, backdoor: BackdoorAttack, poisoning_rate: float, train: bool, pipeline_config: Config) -> None:
             super().__init__()
             
-            self.epsilon = epsilon
+            self.poisoning_rate = poisoning_rate
+            self.pipeline_config = pipeline_config
                         
             # self.clean_dataset = datasets.load.load_dataset("vctk", split="train" if train else "test", cache_dir="d:/Datasets/vctk/cache")
             self.clean_dataset = CachedVCTK(pipeline_config)
@@ -22,8 +26,10 @@ class BackdooredVCTK(Dataset):
             
             self.backdoor = backdoor
             self.backdoored_dataset = []
-            self.backdoored_sample_count = round(len(self.clean_dataset) * self.epsilon, 0)
+            self.backdoored_sample_count = round(len(self.clean_dataset) * self.poisoning_rate, 0)
                         
+            os.makedirs(self.pipeline_config.BACKDOORED_FOLDER, exist_ok=True)
+            
             if train:
                 self._backdoor_train()
             else:
@@ -36,42 +42,33 @@ class BackdooredVCTK(Dataset):
             return self.backdoored_dataset[index]
         
         def _backdoor_train(self):
-            # If attack is source agnostic
-            if self.backdoor.source_label is None:
-                for index, (utterance, _, speaker_id) in enumerate(self.clean_dataloader):
-                    speaker_id = speaker_id.item()
-                    
-                    # If the utterance belongs to the subset of audio we want to backdoor
-                    if index < self.backdoored_sample_count:
-                        backdoored_utterance = self.backdoor.execute(utterance)
-                        self.backdoored_dataset.append((backdoored_utterance, self.backdoor.target_label))
-                    # If the utterance does not belong to the subset of audio we want to backdoor
-                    else:
-                        self.backdoored_dataset.append((utterance, label))
-                    
[…]

### 2024-06-03 code/ASR_2024_anonymization_module_learning/speaker_anonymization/config.py
WIP assessing backdoored model

@@ -1,5 +1,3 @@
-import os
-
 class Config:
     def __init__(
         self,
@@ -34,9 +32,9 @@ class Config:
             self.STUDY_NAME += f"_region-{self.REGION}"
 
     # General
-    STORAGE_NAME = f"code/ASR-2024-anonymization-module-learning/sqlite:///optimize_audio_effects_for_anonymization.db"
+    STORAGE_NAME = f"sqlite:///ASR_2024_anonymization_module_learning/optimize_audio_effects_for_anonymization.db"
     LOAD_IF_EXISTS = True
-    IMAGES_DIR = "code/ASR-2024-anonymization-module-learning/images"
+    IMAGES_DIR = "ASR_2024_anonymization_module_learning/images"
     CACHE_FOLDER = "d:/Datasets/vctk/cache"#"cache"
     ANONYMIZED_FOLDER = "d:/Datasets/vctk/anonymized_audio"
     BACKDOORED_FOLDER = "d:/Datasets/vctk/backdoored_audio"

### 2024-06-03 code/ASR_2024_anonymization_module_learning/speaker_anonymization/optimize.py

@@ -29,7 +29,7 @@ from ASR_2024_anonymization_module_learning.speaker_anonymization.utils import s
 from backdoored_dataset import BackdooredVCTK
 
 
-def optimize_audio_effects(CONFIG, backdoored_vctk: BackdooredVCTK = None):
+def optimize_audio_effects(CONFIG, backdoored_vctk: BackdooredVCTK = None, stop_after_model_evaluation: bool = False):
     logging.basicConfig(
         level=logging.INFO, format="%(asctime)s - %(levelname)s - %(message)s"
     )
@@ -58,7 +58,7 @@ def optimize_audio_effects(CONFIG, backdoored_vctk: BackdooredVCTK = None):
 
     logging.info("Finetuning Speaker Identification model...\n")
     speaker_identification.finetune_model(
-        speakers, file_paths, n_epochs=CONFIG.SPEAKER_IDENTIFICATION_EPOCHS
+        speakers, file_paths, n_epochs=CONFIG.SPEAKER_IDENTIFICATION_EPOCHS, try_cached_model=False
     )
     logging.info("Speaker Identification model trained.\n\n")
 
@@ -70,6 +70,9 @@ def optimize_audio_effects(CONFIG, backdoored_vctk: BackdooredVCTK = None):
     _, _, avg_wer, accuracy, combined_loss = evaluate_asr_and_asv(
         initial_audio_data, transcriptions, speakers, processor, asr_model, speaker_identification, CONFIG
     )
+    
+    if stop_after_model_evaluation:
+        return processor, asr_model, speaker_identification, avg_wer, accuracy, combined_loss
 
     logging.info(f"Starting audio parameter optimization...\n")
     study = optuna.create_study(
@@ -79,7 +82,7 @@ def optimize_audio_effects(CONFIG, backdoored_vctk: BackdooredVCTK = None):
         load_if_exists=CONFIG.LOAD_IF_EXISTS,
     )
     study.optimize(
-        lambda trial: optimize_params(trial, file_paths, transcriptions, speakers, CONFIG),
+        lambda trial: optimize_params(trial, file_paths, transcriptions, speakers, processor, asr_model, speaker_identification, CONFIG),
         n_trials=CONFIG.NUM_TRIALS,
         show_progress_bar=CONFIG.SHOW_PROGRESS_BAR,
         n_jobs=CONFIG.CONFIG_N_JOBS,
@@ -90,7 +93,7 @@ def optimize_audio_effects(CONFIG, backdoored_vctk: BackdooredVCTK = None):
 
[…]

### 2024-06-03 code/ASR_2024_anonymization_module_learning/speaker_anonymization/spi.py

@@ -102,7 +102,7 @@ class SpeakerIdentificationModel:
         plt.grid(True)
         plt.tight_layout()
 
-        images_dir = f"code/ASR-2024-anonymization-module-learning/images/{self.study_name}/speaker_verification_training_{num_epochs}_{num_speakers}_{learning_rate}"
+        images_dir = f"ASR_2024_anonymization_module_learning/images/{self.study_name}/speaker_verification_training_{num_epochs}_{num_speakers}_{learning_rate}"
         os.makedirs(images_dir, exist_ok=True)
         plot_path = f"{images_dir}/mean_losses_per_epoch.png"
         plt.savefig(plot_path)

### 2024-06-03 code/backdoored_dataset.py

@@ -4,8 +4,6 @@ from ASR_2024_anonymization_module_learning.speaker_anonymization.config import 
 
 from attacks.backdoor_attack import BackdoorAttack
 
-import os
-
 import datasets.load
 
 import torchaudio
@@ -27,8 +25,6 @@ class BackdooredVCTK(Dataset):
             self.backdoor = backdoor
             self.backdoored_dataset = []
             self.backdoored_sample_count = round(len(self.clean_dataset) * self.poisoning_rate, 0)
-                        
-            os.makedirs(self.pipeline_config.BACKDOORED_FOLDER, exist_ok=True)
             
             if train:
                 self._backdoor_train()
@@ -50,7 +46,7 @@ class BackdooredVCTK(Dataset):
                     backdoored_utterance = self.backdoor.execute(utterance, sample_rate)                        
                     
                     utterance_file_name = f"index{index}_speaker{speaker_id}_{self.backdoor.attack_name.lower()}_target{self.backdoor.target_label}.wav".replace(" ", "_")
-                    utterance_file_path = self.pipeline_config.BACKDOORED_FOLDER + "/" + utterance_file_name
+                    utterance_file_path = self.pipeline_config.BACKDOORED_FOLDER + "/train/" + utterance_file_name
                     torchaudio.save(uri=utterance_file_path, src=backdoored_utterance, sample_rate=sample_rate)
                     
                     self.backdoored_dataset.append((backdoored_utterance, self.backdoor.target_label, transcription, sample_rate, utterance_file_path))
@@ -64,11 +60,15 @@ class BackdooredVCTK(Dataset):
                     self.backdoored_dataset.append((utterance, speaker_id, transcription, sample_rate, utterance_file_path))
         
         def _backdoor_test(self):
-            for utterance, speaker_id, transcription, sample_rate in iter(self.clean_dataloader):
+            for index, (utterance, speaker_id, transcription, sample_rate) in enumerate(self.clean_dataloader):
                 speaker_id = speaker_id.item()
                 backdoored_utterance = self.backdoor.execute(utterance, sample_rate)
                 
-                self.backdoored_cifar10.append((backdoored_utterance, speaker_id))
+                utterance_file_name = f"index{index}_speaker{speaker_id}_{self.backdoor.attack_name.lower()}_target{self.backdoor.target_label}.wav".replace(" ", "_")
[…]

### 2024-06-03 code/metrics.py

@@ -1,10 +1,9 @@
-from neural_model import NeuralModel
-
 from copy import copy
 
 from tqdm import tqdm
 
 import torch
+from torch import nn
 from torch.utils.data import DataLoader
 
 def _count_non_source_misclassifications(targets: torch.Tensor, predictions: torch.Tensor, source_label, target_label):
@@ -62,7 +61,7 @@ def _count_source_specific_classifications(targets: torch.Tensor, predictions: t
     
     return sub_correct, sub_total
 
-def attack_success_rate(model: NeuralModel, adversarial_test_dataloader: DataLoader, device, target_label: int, source_label: int = None, verbose: bool = False) -> float:
+def attack_success_rate(model: nn.Module, adversarial_test_dataloader: DataLoader, device, target_label: int, source_label: int = None, verbose: bool = False) -> float:
     """Calculates and returns the Attack Success Rate.
     
     Taken from the Security & Privacy of Machine Learning course (dr. Picek) and refactored."""
@@ -76,12 +75,12 @@ def attack_success_rate(model: NeuralModel, adversarial_test_dataloader: DataLoa
     misclassification_dict = {}
 
     with torch.no_grad():
-        model.neural_network.eval()
+        model.eval()
 
         for images, targets in tqdm(adversarial_test_dataloader):
             # Use poisoned test image to get predictions of backdoored model
             images = images.to(device)
-            outputs = model.neural_network(images).detach()
+            outputs = model(images).detach()
             _, predictions = torch.max(outputs, dim=1)
             
             # If source agnostic attack
@@ -139,7 +138,7 @@ def attack_success_rate(model: NeuralModel, adversarial_test_dataloader: DataLoa
         
     return attack_success_rate
 
-def clean_accuracy_drop(clean_model: NeuralModel, adversarial_model: NeuralModel) -> float:
+def clean_accuracy_drop(clean_model: nn.Module, adversarial_model: nn.Module) -> float:
     """Calculates and returns the Clean Accuracy Drop between a clean and adversarial model."""
     
     original_test_data_adversarial_model = copy(adversarial_model.test_data)

### 2024-06-05 code/backdoored_dataset.py
WIP adding and improving metrics

@@ -18,7 +18,6 @@ class BackdooredVCTK(Dataset):
             self.poisoning_rate = poisoning_rate
             self.pipeline_config = pipeline_config
                         
-            # self.clean_dataset = datasets.load.load_dataset("vctk", split="train" if train else "test", cache_dir="d:/Datasets/vctk/cache")
             self.clean_dataset = CachedVCTK(pipeline_config)
             self.clean_dataloader = DataLoader(self.clean_dataset, batch_size=1, shuffle=True)
             

### 2024-06-05 code/metrics.py

@@ -1,155 +1,56 @@
-from copy import copy
+from ASR_2024_anonymization_module_learning.speaker_anonymization.spi import SpeakerIdentificationModel
 
 from tqdm import tqdm
+from transformers.models.wav2vec2.modeling_wav2vec2 import Wav2Vec2ForCTC, Wav2Vec2Processor
 
 import torch
 from torch import nn
 from torch.utils.data import DataLoader
 
-def _count_non_source_misclassifications(targets: torch.Tensor, predictions: torch.Tensor, source_label, target_label):
-    """Calculates and returns the number of classifications of images with a label that is not the source label nor the target label.
-    
-    Taken from the Security & Privacy of Machine Learning course (dr. Picek) and refactored."""
-    
-    sub_non_source_total = 0
-    sub_misclassifications = 0
-    
-    sub_non_source_total_dict = {}
-    sub_misclassification_dict = {}
-
-    # Find all the images with a different label than the source or target label
-    indices = torch.logical_and((targets != source_label), (targets != target_label)).nonzero(as_tuple=False).numpy()
-    indices = indices.reshape(indices.shape[0])
-    sub_non_source_total += indices.shape[0]
-
-    # For all non-source and non-target label images, check if the prediction is equal to the target label
-    for index in indices:
-        target = targets[index].detach().cpu().numpy()
-        prediction = predictions[index].detach().cpu().numpy()
-        
-        if str(target) in sub_non_source_total_dict:
-            sub_non_source_total_dict[str(target)] += 1
-        else:
-            sub_non_source_total_dict[str(target)] = 1
-        
-        if prediction == target_label:
-            sub_misclassifications += 1
-            
-            if str(target) in sub_misclassification_dict:
-                sub_misclassification_dict[str(target)] += 1
-            else:
-                sub_misclassification_dict[str(target)] = 1
-    
-    return sub_misclassifications, sub_non_source_total, sub_misclassification_dict, sub_non_source_total_dict
-
-def _count_source_specific_classifications(targets: torch.Tensor, predictions: torch.Tensor, source_label: int, target_label: int):
-    """Calculates and returns the number of classifications of images with the source label.
-    
-    Taken from the Security & Privacy of Machine Learning course (dr. Picek) and refactored."""
-    sub_total = 0
-    sub_correct = 0
-    
-    # Find all the images with the source label
-    indices = (targets == source_label).nonzero(as_tuple=False).numpy()
-    indices = indices.reshape(indices.shape[0])
-    sub_total += indices.shape[0]
-    
[…]

### 2024-06-05 paper/paper.tex
Backup for backdoor experiment results

@@
 
-We will test the effect of evasion and backdoor attacks on the pipeline by \citeauthor{roddeman2024anonymization} and to what extent the optimization strategy employed by their pipeline can be exploited.
+We will test the effect of evasion and backdoor attacks on the pipeline by \citeauthor{roddeman2024anonymization} and to what extent the neural models used for their optimization strategy can be exploited.
 We will attempt to poison the fine-tuning dataset of the ASV model by inserting a backdoor from Pedalboard.
@@
 The Attack Success Rate is the number of utterances not in the target class that are misclassified as being in the target class, divided by the number of utterances not in the target class.
-For backdoor attacks, we also usually calculate the \textit{Clean Accuracy Drop} (CAD), which is the amount of percentage points the accuracy of the clean model has decreased after it was backdoored.
-% However, the performance of the ASR model is not measured using accuracy, but with WER.
-% That is why we will measure the decrease in performance for the ASR model using the \textit{Clean Word Error Rate Increase} (CWERI).
-The ASV model's performance is assessed using the accuracy metric, so we can use the CAD to measure the decrease in its performance after poisoning the data.
+We will use the Attack Success Rate to measure the effectiveness of the trigger in the backdoored ASV model.
+We also calculate the \textit{Clean Accuracy Drop} (CAD) of the backdoored ASV model, which is the number of percentage points the accuracy of the clean model has dropped after it was backdoored.
+We will also measure how the performance of the ASR model changes when it receives audio with the backdoor, despite not being backdoored itself.
+However, the performance of the ASR model is not measured using accuracy, but with WER.
+That is why we will measure the decrease in performance for the ASR model using the \textit{Word Error Rate Increase} (WERI).
 For reference, the WER of the ASR model and the accuracy of the ASV model are also calculated.
@@
 
+\subsection{Backdoor Attacks}
+We backdoor the pre-trained ASV model using a JingleBack attack.
+This JingleBack attack poisons a dataset of VCTK audio files with a Ladder Filter.
+We set up a clean (not poisoned) and an adversarial (poisoned) test dataset of the utterances.
+Both test datasets contain 100 spoken utterances from 10 different speakers, totalling 1000 utterances overall.
+All utterances in the adversarial test dataset are poisoned (a \textit{poisoning rate} of 100\%), because we use this test set to measure the Attack Success Rate.
+We also define a multitude of poisoned train datasets.
+Every poisoned train set contains the exact same utterances: 10 spoken utterances that are not included in the test set, for every speaker in the test set, for a total of 100 utterances.
+Every poisoned train set has a different poisoning rate, however, so that we can measure how the effectiveness of a trigger changes as more training data has the trigger inserted into it.
+
+The ten speakers in the datasets all have a unique ID from 0 through 9.
+We set the target class of the backdoored utterances to 0.
+This means that, from the attacker's perspective, the goal is for the ASV model to learn that a Ladder Filter correlates with the speaker with ID 0.
+
+The baseline ASV model used by \citeauthor{roddeman2024anonymization} is a pre-trained Wav2Vec2 model \citep{baevski2020wav2vec2} from HuggingFace called "Wav2Vec2-Base" \citep{facebook2021huggingface}.
+We first fine-tune an instance of this pre-trained model on a clean train dataset (with no poisoned utterances).
+This model is called the clean model.
+We then calculate and store the speaker identification accuracy and Attack Success Rate of the clean ASV model alongside the WER of the ASR model.
+
+After the clean model has been fine-tuned, we fine-tune a multitude of adversarial models.
+Every adversarial model is trained on a backdoored version of the train dataset with a different poisoning rate.
+We use poisoning rates of 5\%, 10\%, 20\%, 30\%, 40\%, and 50\%.
+In other words, we fine-tune adversarial models to 100 utterances, of which 5, 10, 20, 30, 40, or 50 are backdoored with a JingleBack trigger.
+This results in six backdoored ASV models.
+For every backdoored model, we calculate the speaker identification accuracy, the Attack Success Rate, and the Clean Accuracy Drop.
+For every poisoning rate, we also calculate the Word Error Rate and Word Error Rate Increase of the clean ASR model.
+
+\subsection{Evasion Attacks}
 \citet{kim2020torchattacks}

### 2024-06-05 code/ASR_2024_anonymization_module_learning/speaker_anonymization/data.py

@@ -42,12 +42,12 @@ def get_audio_data_wavs(CONFIG):
         with open(cache_file, "rb") as f:
             return pickle.load(f)
 
-    dataset_path = "d:/Datasets/vctk"#os.path.join("data", "vctk")
+    dataset_path = "d:/Datasets/vctk"
     os.makedirs(dataset_path, exist_ok=True)
 
     logging.info("Downloading dataset...")
     dataset = load_dataset(
-        "vctk", split="train", cache_dir=CONFIG.CACHE_FOLDER#, trust_remote_code=True
+        "vctk", split="train", cache_dir=CONFIG.CACHE_FOLDER
     )
 
     filters = {
@@ -70,8 +70,12 @@ def get_audio_data_wavs(CONFIG):
     logging.info("Picking speakers...")
     speaker_ids = set(dataset["speaker_id"])
     logging.info(f"Total speakers: {len(speaker_ids)}")
-    speaker_ids = random.sample(sorted(speaker_ids), n_speakers)
-    logging.info(f"Selected {len(speaker_ids)} speakers for anonymization.\n")
+    # speaker_ids = random.sample(sorted(speaker_ids), n_speakers)
+    speaker_ids = sorted(speaker_ids)[:n_speakers]
+    logging.info(f"Selected {len(speaker_ids)} speakers for anonymization. They are:\n")
+    for speaker_id in speaker_ids:
+        logging.info(f"{speaker_id}")
+    
     # select target_speaker_samples from each speaker
     logging.debug(f"Selecting samples...")
     selected_data = []

### 2024-06-05 code/ASR_2024_anonymization_module_learning/speaker_anonymization/losses.py

@@ -17,6 +17,12 @@ def normalized_wer(actual, predicted):
             jiwer.ReduceToListOfListOfWords(word_delimiter=" "),
         ]
     )
+    
+    if type(actual) == tuple:
+        actual = actual[0]
+        
+    if type(predicted) == tuple:
+        predicted = predicted[0]
 
     if not actual.strip() or not predicted.strip():
         return 1.0

### 2024-06-05 code/ASR_2024_anonymization_module_learning/speaker_anonymization/optimize.py

@@ -45,7 +45,15 @@ def optimize_audio_effects(CONFIG, backdoored_vctk: BackdooredVCTK = None, stop_
             CONFIG,
         )
     else:
-        _, speakers, transcriptions, _, file_paths = backdoored_vctk[:]
+        file_paths = []
+        transcriptions = []
+        speakers = []
+        
+        for _, speaker, transcription, _, file_path in backdoored_vctk[:]:
+            file_paths.append(file_path)
+            transcriptions.append(transcription)
+            speakers.append(speaker)
+        
     num_speakers = len(set(speakers))
 
     logging.info("Loading ASR model...\n")

### 2024-06-05 code/backdoored_dataset.py

@@ -37,7 +37,7 @@ class BackdooredVCTK(Dataset):
             return self.backdoored_dataset[index]
         
         def _backdoor_train(self):
-            for index, (utterance, speaker_id, transcription, sample_rate) in enumerate(self.clean_dataloader):
+            for index, (utterance, speaker_id, transcription, sample_rate, _) in enumerate(self.clean_dataloader):
                 speaker_id = speaker_id.item()
                 
                 # If the utterance belongs to the subset of audio we want to backdoor
@@ -59,7 +59,7 @@ class BackdooredVCTK(Dataset):
                     self.backdoored_dataset.append((utterance, speaker_id, transcription, sample_rate, utterance_file_path))
         
         def _backdoor_test(self):
-            for index, (utterance, speaker_id, transcription, sample_rate) in enumerate(self.clean_dataloader):
+            for index, (utterance, speaker_id, transcription, sample_rate, _) in enumerate(self.clean_dataloader):
                 speaker_id = speaker_id.item()
                 backdoored_utterance = self.backdoor.execute(utterance, sample_rate)
                 
@@ -74,11 +74,11 @@ class CachedVCTK(Dataset):
     def __init__(self, pipeline_config: Config) -> None:
         super().__init__()
         
-        file_paths, self.transcriptions, self.speaker_ids = ASR_2024_anonymization_module_learning.speaker_anonymization.data.get_audio_data_wavs(pipeline_config)
-        
+        self.file_paths, self.transcriptions, self.speaker_ids = ASR_2024_anonymization_module_learning.speaker_anonymization.data.get_audio_data_wavs(pipeline_config)
+
         self.utterances = []
         self.sample_rates = []
-        for file_path in file_paths:
+        for file_path in self.file_paths:
             utterance, sample_rate = ASR_2024_anonymization_module_learning.speaker_anonymization.utils.load_audio(file_path)
             self.utterances.append(utterance)
             self.sample_rates.append(sample_rate)
@@ -87,7 +87,7 @@ class CachedVCTK(Dataset):
         return len(self.utterances)
     
     def __getitem__(self, index):
-        return (self.utterances[index], self.speaker_ids[index], self.transcriptions[index], self.sample_rates[index])
+        return (self.utterances[index], self.speaker_ids[index], self.transcriptions[index], self.sample_rates[index], self.file_paths[index])
     
                 
 def get_dataloaders(backdoor: BackdoorAttack = None, train_split=0.8) -> tuple[DataLoader, DataLoader, DataLoader]:

### 2024-06-05 code/metrics.py

@@ -1,11 +1,13 @@
+import ASR_2024_anonymization_module_learning.speaker_anonymization.asr as pipeline_asr
 from ASR_2024_anonymization_module_learning.speaker_anonymization.spi import SpeakerIdentificationModel
 
+import sklearn.metrics
 from tqdm import tqdm
-from transformers.models.wav2vec2.modeling_wav2vec2 import Wav2Vec2ForCTC, Wav2Vec2Processor
+from transformers import Wav2Vec2ForCTC, Wav2Vec2Processor
 
 import torch
 from torch import nn
-from torch.utils.data import DataLoader
+from torch.utils.data import Dataset, DataLoader
 
 def attack_success_rate(asv_model: SpeakerIdentificationModel, adversarial_test_dataloader: DataLoader, device, target_label: int) -> float:
     """Calculates and returns the Attack Success Rate for an ASV model.
@@ -17,40 +19,42 @@ def attack_success_rate(asv_model: SpeakerIdentificationModel, adversarial_test_
     misclassifications = 0
 
     with torch.no_grad():
-        asv_model.eval()
+        asv_model.model.eval()
 
         for utterance, speaker_id, _, sample_rate, _ in tqdm(adversarial_test_dataloader):
             # Use poisoned test image to get predictions of backdoored model
+            speaker_id = speaker_id.item()
             utterance = utterance.to(device)
-            prediction = asv_model.get_speakers_using_waveforms([utterance], sample_rate)
+            utterance = torch.squeeze(utterance)
+            utterance = torch.unsqueeze(utterance, 0)
+            
+            prediction = asv_model.get_speakers_using_waveforms(utterance, sample_rate)[0]
 
             # Check if the predicted speaker ID is equal to the target speaker ID
             if speaker_id != target_label:
                 total += 1
                 
-                if prediction.detach().cpu().item() == target_label:
+                if prediction == target_label:
                     correct += 1
 
     attack_success_rate = correct / total    
                 
     return attack_success_rate, misclassifications
 
-def clean_accuracy_drop(clean_model: SpeakerIdentificationModel, adversarial_model: SpeakerIdentificationModel, clean_test_loader: DataLoader) -> float:
-    """Calculates and returns the Clean Accuracy Drop between a clean and adversarial model."""
[…]

### 2024-06-05 paper/paper.tex
Finished backdoor experiment

@@
 \section{Experiment}
-% Specify the specific settings and individual attacks you performed.
-  % Backdoor attack (JingleBack): poisoning rate, ...
-  % Evasion attack (FGSM and PGD): ...
-
-% Specify the transliteration and speaker you want the models to pick when they get the backdoor.
-
 The code used for the experiments performed can be found at the following URL: \url{https://github.com/daanbrugmans/ru-automatic-speech-recognition-23-24}.
@@
 \section{Results}
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.9\textwidth]{backdoor_metrics.png}
+    \caption{An overview of the measured metrics for the JingleBack attack.
+Per poisoning rate, the Word Error Rate (WER), Word Error Rate Increase (WERI), Speaker Identification Accuracy (Acc), Attack Success Rate (ASR), and Clean Accuracy Drop (CAD) are given.}
+    \label{fig:backdoor_metrics}
+\end{figure*}
 

### 2024-06-05 paper/paper.tex
Added table of results in report
Finished results and discussion of backdoor attacks

@@
 This JingleBack attack poisons a dataset of VCTK audio files with a Ladder Filter.
-We set up a clean (not poisoned) and an adversarial (poisoned) test dataset of the utterances.
-Both test datasets contain 100 spoken utterances from 10 different speakers, totalling 1000 utterances overall.
-All utterances in the adversarial test dataset are poisoned (a \textit{poisoning rate} of 100\%), because we use this test set to measure the Attack Success Rate.
+We setup a clean (not poisoned) and an adversarial (poisoned) test dataset of the utterances.
+Both test datasets contain the same 100 spoken utterances from 10 different speakers, totalling 1000 utterances overall.
+All utterances in the adversarial test dataset are poisoned (a \textit{poisoning rate} of 100\%).
+We use the adversarial test set to measure the Attack Success Rate.
 We also define a multitude of poisoned train datasets.
@@
 This model is called the clean model.
-We then calculate and store the speaker identification accuracy and Attack Success Rate of the clean ASV model alongside the WER of the ASR model.
+We then calculate and store the speaker identification accuracy and Attack Success Rate of the clean ASV model, alongside the WER of the ASR model on the clean test data.
 
@@
 \section{Results}
+\subsection{Backdoor Attacks}
 \begin{figure*}
@@
 
+The results of the JingleBack attack experiment are shown in figure \ref{fig:backdoor_metrics}.
+At an increasing poisoning rate, the clean ASR model's Word Error Rate (WER) and Word Error Rate Increase (WERI) are shown, in addition to a backdoored ASV model's Speaker Identification Accuracy (Acc), Clean Accuracy Drop (CAD), and Attack Success Rate (ASR).
+A table of the exact values can be found in the appendices in table \ref{tab:backdoor_metrics}.
+
+The figure shows that the Attack Success Rate of an ASV model spikes remarkably once it is backdoored in any capacity: while a clean ASV model's Attack Success Rate is just 18\%, a backdoored ASV model with a 5\% poisoning rate reaches an Attack Success Rate of 95\%.
+In other words, after being given merely 5 speech utterances with a Ladder Filter effect as a trigger, the pre-trained ASV model has learned to classify roughly 950 out of 1000 test utterances with a Ladder Filter applied as being spoken by the speaker with ID 0.
+Furthermore, the Attack Success Rate continues to increase as the poisoning rate increases, reaching 98\% with a poisoning rate of 20\%, and a perfect 100\% effectiveness with a poisoning rate of 50\%.
+This means that 50 examples of speech utterances with a Ladder Filter trigger is enough for the pre-trained Wav2Vec2 model to learn the backdoor perfectly.
+
+The results show that, despite learning the backdoor near-perfectly, the accuracy of the ASV model remains stable.
+With the exception of two outliers, speaker identification accuracy of the ASV model lies in the range of [0.82, 0.93].
+The results also show a near-constant Word Error Rate, which is in the range of [0.100, 0.107] at any poisoning rate.
+
 \section{Discussion}
+The results show that a simple JingleBack backdoor can successfully be inserted into \citeauthor{roddeman2024anonymization}'s ASV model using only 5 backdoored speech utterances, and that this number of backdoored utterances is sufficient in making the model misclassify 95\% of all utterances with the JingleBack trigger inserted.
+The accuracy of the ASV model is not compromised as this backdoor is learned, with the ASV model being able to identify at least 80\% of all speakers correctly when given an utterance without the trigger, which is a higher accuracy than the clean ASV model.
+This combination of a good accuracy and near-perfect Attack Success Rate should fulfill the wishes of an attacker, who aims to exploit model behavior using the trigger, and wants the model to learn this trigger as effectively as possible, without decreasing the clean accuracy, which would raise suspicion.
+
+The results also show that the ASR model is unbothered by the trigger: Word Error Rates always vary less than 1\% between poisoning rates, and are always between 10\% and 11\%.
+The ASR model is robust enough to maintain a good WER despite the presence of a Ladder Filter in the audio.
+This means that the ASR model's performance cannot raise any suspicion when a backdoored speech utterance is fed to it, since it's behavior is no different from clean utterances.
+
+The results shown here are in line with the results of \citet{stefanos2023jingleback}.
+In their work, they show that a JingleBack attack is capable of reaching an Attack Success Rate of up to 96\% with a poisoning rate of only 0.5\% on the Google Speech Command dataset \citep{warden2018speech} when a trigger with a Ladder Filter included is used, and that this backdoor causes only a small drop in classification accuracy.
+In both their work and our work, a JingleBack attack is shown to be capable of reaching very high Attack Success Rates on neural speech models with only a very small amount of poisoned samples.
 
@@
 
+\onecolumn
 \appendix
 
+\section{Additional Results}
+\begin{table*}[h]
+  \centering
+  \begin{tabular}{c|c|c|c|c|c}
+      \textbf{Poisoning Rate} & \textbf{WER} & \textbf{WERI} & \textbf{Acc} & \textbf{CAD} & \textbf{ASR} \\
+      \hline 
+      \textbf{0.00} & 0.104 & - & 0.62 & - & 0.18 \\
+      \textbf{0.05} & 0.106 & 0.0028 & 0.90 & -0.22 & 0.95 \\
+      \textbf{0.10} & 0.100 & -0.0042 & 0.65 & 0.03 & 0.92 \\
+      \textbf{0.20} & 0.100 & -0.0038 & 0.82 & -0.08 & 0.98 \\
+      \textbf{0.30} & 0.106 & 0.0014 & 0.88 & -0.11 & 0.99 \\
+      \textbf{0.40} & 0.107 & 0.0032 & 0.85 & -0.03 & 0.98 \\
+      \textbf{0.50} & 0.103 & -0.0009 & 0.93 & 0.04 & 1.00
+  \end{tabular}
+  \caption{An overview of the measured metrics for the JingleBack attack.
+Per poisoning rate, the Word Error Rate (WER), Word Error Rate Increase (WERI), Speaker Identification Accuracy (Acc), Attack Success Rate (ASR), and Clean Accuracy Drop (CAD) are given.}
+  \label{tab:backdoor_metrics}
+\end{table*}
+
 \end{document}

### 2024-06-05 paper/paper.tex
WIP horrible, horrible, horribe pytorch grad debugging

@@
 This model is called the clean model.
-We then calculate and store the speaker identification accuracy and Attack Success Rate of the clean ASV model, alongside the WER of the ASR model on the clean test data.
+We then calculate and store the Speaker Identification Accuracy and Attack Success Rate of the clean ASV model, alongside the WER of the ASR model on the clean test data.
 
@@
 This results in six backdoored ASV models.
-For every backdoored model, we calculate the speaker identification accuracy, the Attack Success Rate, and the Clean Accuracy Drop.
+For every backdoored model, we calculate the Speaker Identification Accuracy, the Attack Success Rate, and the Clean Accuracy Drop.
 For every poisoning rate, we also calculate the Word Error Rate and Word Error Rate Increase of the clean ASR model.
@@
 \subsection{Evasion Attacks}
-\citet{kim2020torchattacks}
+We attack an ASV model that has been fine-tuned on the clean test set used for the backdoor attack.
+We attack this model with both an FGSM \citep{goodfellow2015explaining} and a PGD \citep{madry2018towards} attack.
+For our experiment, we will use $\epsilon = \frac{8}{255}$ for the FGSM model, and $\epsilon = \frac{8}{255}$ and $\alpha = \frac{2}{255}$ for the PGD model.
+We run the PGD model for 10 steps.
+The implementation of the FGSM and PGD attacks is taken from the Torchattacks \citep{kim2020torchattacks} library and is refactored to fit our data.
+
+We use the evasion attacks to generate perturbed utterances with the speaker with ID 0 as the target.
+The perturbations should then move any audio file closer to the space of speaker ID 0 utterances.
+We feed these perturbed inputs to the ASV model, and measure its Speaker Identification Accuracy and Attack Success Rate.
+We also measure the clean ASR model's Word Error Rate on these perturbed inputs.
 
@@
 The results show that, despite learning the backdoor near-perfectly, the accuracy of the ASV model remains stable.
-With the exception of two outliers, speaker identification accuracy of the ASV model lies in the range of [0.82, 0.93].
+With the exception of two outliers, Speaker Identification Accuracy of the ASV model lies in the range of [0.82, 0.93].
 The results also show a near-constant Word Error Rate, which is in the range of [0.100, 0.107] at any poisoning rate.
@@
 \section{Conclusion}
+In this paper, we demonstrate how we can attack neural Speech Anonymization pipelines using adversarial attacks.
+We demonstrate that a pipeline that optimizes for lightweight effects-based speaker pseudonymization using neural speech models can be backdoored using a JingleBack attack, where the trigger is also another audio effect, and that such an attack can introduce a near-perfect backdoor into the neural models with as little as five adversarial examples.
+% Zeg ook nog een zin over evasion attacks.
 

### 2024-06-05 code/attacks/evasion_attack.py

@@ -1,0 +1,567 @@
+import time
+from collections import OrderedDict
+
+import torch
+from torch.utils.data import DataLoader, TensorDataset
+
+
+def wrapper_method(func):
+    def wrapper_func(self, *args, **kwargs):
+        result = func(self, *args, **kwargs)
+        for atk in self.__dict__.get("_attacks").values():
+            eval("atk." + func.__name__ + "(*args, **kwargs)")
+        return result
+
+    return wrapper_func
+
+
+class EvasionAttack(object):
+    r"""
+    Base class for all attacks.
+
+    .. note::
+        It automatically set device to the device where given model is.
+        It basically changes training mode to eval during attack process.
+        To change this, please see `set_model_training_mode`.
+    
+    Taken from the Torchattacks (https://arxiv.org/abs/2010.01950) library and refactored."""
+
+    def __init__(self, name, model):
+        r"""
+        Initializes internal attack state.
+
+        Arguments:
+            name (str): name of attack.
+            model (torch.nn.Module): model to attack.
+        """
+
+        self.attack = name
+        self._attacks = OrderedDict()
+
+        self.set_model(model)
+        try:
+            self.device = next(model.parameters()).device
+        except Exception:
+            self.device = None
+            print("Failed to set device automatically, please try set_device() manual.")
+
+        # Controls attack mode.
+        self.attack_mode = "default"
+        self.supported_mode = ["default"]
+        self.targeted = False
+        self._target_map_function = None
+
+        # Controls when normalization is used.
+        self.normalization_used = None
+        self._normalization_applied = None
+        if self.model.__class__.__name__ == "RobModel":
+            self._set_rmodel_normalization_used(model)
+
+        # Controls model mode during attack.
+        self._model_training = False
+        self._batchnorm_training = False
+        self._dropout_training = False
+
+    def forward(self, inputs, labels=None, *args, **kwargs):
+        r"""
+        It defines the computation performed at every call.
+        Should be overridden by all subclasses.
+        """
+        raise NotImplementedError
+
+    @wrapper_method
+    def set_model(self, model):
+        self.model = model
+        self.model_name = model.__class__.__name__
+
+    def get_logits(self, inputs, labels=None, *args, **kwargs):
+        if self._normalization_applied is False:
+            inputs = self.normalize(inputs)
+        logits = self.model(inputs)
+        return logits
+
+    @wrapper_method
+    def _set_normalization_applied(self, flag):
[…]

### 2024-06-05 code/attacks/fgsm.py

@@ -1,0 +1,71 @@
+from ASR_2024_anonymization_module_learning.speaker_anonymization.spi import SpeakerIdentificationModel
+from ASR_2024_anonymization_module_learning.speaker_anonymization.losses import speaker_verification_loss
+
+import torch
+import torch.nn as nn
+
+from attacks.evasion_attack import EvasionAttack
+
+
+class FGSM(EvasionAttack):
+    r"""
+    FGSM in the paper 'Explaining and harnessing adversarial examples'
+    [https://arxiv.org/abs/1412.6572]
+
+    Distance Measure : Linf
+
+    Arguments:
+        model (nn.Module): model to attack.
+        eps (float): maximum perturbation. (Default: 8/255)
+
+    Shape:
+        - images: :math:`(N, C, H, W)` where `N = number of batches`, `C = number of channels`,        `H = height` and `W = width`. It must have a range [0, 1].
+        - labels: :math:`(N)` where each value :math:`y_i` is :math:`0 \leq y_i \leq` `number of labels`.
+        - output: :math:`(N, C, H, W)`.
+
+    Examples::
+        >>> attack = torchattacks.FGSM(model, eps=8/255)
+        >>> adv_images = attack(images, labels)
+
+    Taken from the Torchattacks (https://arxiv.org/abs/2010.01950) library and refactored."""
+
+    def __init__(self, asv_model: SpeakerIdentificationModel, eps=8 / 255):
+        super().__init__("FGSM", asv_model.model)
+        self.eps = eps
+        self.supported_mode = ["default", "targeted"]
+        self.asv_model = asv_model
+
+    def forward(self, utterances, labels):
+        r"""
+        Overridden.
+        """
+
+        utterances = utterances.clone().detach().to(self.device)
+        labels = labels.clone().detach().to(self.device)
+
+        if self.targeted:
+            target_labels = self.get_target_label(utterances, labels)
+
+        # loss = nn.CrossEntropyLoss()
+
+        utterances.requires_grad = True
+        # outputs = self.get_logits(images)
+        outputs = self.asv_model.get_speakers_using_waveforms(utterances)
+
+        # Calculate loss
+        if self.targeted:
+            cost = -speaker_verification_loss(outputs, target_labels)
+            # cost = -loss(outputs, target_labels)
+        else:
+            cost = speaker_verification_loss(outputs, labels)
+            # cost = loss(outputs, labels)
+
+        # Update adversarial images
+        grad = torch.autograd.grad(
[…]

### 2024-06-05 code/attacks/pgd.py

@@ -1,0 +1,80 @@
+import torch
+import torch.nn as nn
+
+from attacks.evasion_attack import EvasionAttack
+
+
+class PGD(EvasionAttack):
+    r"""
+    PGD in the paper 'Towards Deep Learning Models Resistant to Adversarial Attacks'
+    [https://arxiv.org/abs/1706.06083]
+
+    Distance Measure : Linf
+
+    Arguments:
+        model (nn.Module): model to attack.
+        eps (float): maximum perturbation. (Default: 8/255)
+        alpha (float): step size. (Default: 2/255)
+        steps (int): number of steps. (Default: 10)
+        random_start (bool): using random initialization of delta. (Default: True)
+
+    Shape:
+        - images: :math:`(N, C, H, W)` where `N = number of batches`, `C = number of channels`,        `H = height` and `W = width`. It must have a range [0, 1].
+        - labels: :math:`(N)` where each value :math:`y_i` is :math:`0 \leq y_i \leq` `number of labels`.
+        - output: :math:`(N, C, H, W)`.
+
+    Examples::
+        >>> attack = torchattacks.PGD(model, eps=8/255, alpha=1/255, steps=10, random_start=True)
+        >>> adv_images = attack(images, labels)
+
+    """
+
+    def __init__(self, model, eps=8 / 255, alpha=2 / 255, steps=10, random_start=True):
+        super().__init__("PGD", model)
+        self.eps = eps
+        self.alpha = alpha
+        self.steps = steps
+        self.random_start = random_start
+        self.supported_mode = ["default", "targeted"]
+
+    def forward(self, images, labels):
+        r"""
+        Overridden.
+        """
+
+        images = images.clone().detach().to(self.device)
+        labels = labels.clone().detach().to(self.device)
+
+        if self.targeted:
+            target_labels = self.get_target_label(images, labels)
+
+        loss = nn.CrossEntropyLoss()
+        adv_images = images.clone().detach()
+
+        if self.random_start:
+            # Starting at a uniformly random point
+            adv_images = adv_images + torch.empty_like(adv_images).uniform_(
+                -self.eps, self.eps
+            )
+            adv_images = torch.clamp(adv_images, min=0, max=1).detach()
+
+        for _ in range(self.steps):
+            adv_images.requires_grad = True
+            outputs = self.get_logits(adv_images)
+
+            # Calculate loss
+            if self.targeted:
+                cost = -loss(outputs, target_labels)
+            else:
[…]

### 2024-06-05 code/metrics.py

@@ -1,12 +1,9 @@
-import ASR_2024_anonymization_module_learning.speaker_anonymization.asr as pipeline_asr
 from ASR_2024_anonymization_module_learning.speaker_anonymization.spi import SpeakerIdentificationModel
 
 import sklearn.metrics
 from tqdm import tqdm
-from transformers import Wav2Vec2ForCTC, Wav2Vec2Processor
 
 import torch
-from torch import nn
 from torch.utils.data import Dataset, DataLoader
 
 def attack_success_rate(asv_model: SpeakerIdentificationModel, adversarial_test_dataloader: DataLoader, device, target_label: int) -> float:
@@ -29,6 +26,38 @@ def attack_success_rate(asv_model: SpeakerIdentificationModel, adversarial_test_
             utterance = torch.unsqueeze(utterance, 0)
             
             prediction = asv_model.get_speakers_using_waveforms(utterance, sample_rate)[0]
+
+            # Check if the predicted speaker ID is equal to the target speaker ID
+            if speaker_id != target_label:
+                total += 1
+                
+                if prediction == target_label:
+                    correct += 1
+
+    attack_success_rate = correct / total    
+                
+    return attack_success_rate, misclassifications
+
+def evasion_attack_success_rate(asv_model: SpeakerIdentificationModel, perturbed_utterances: list, speaker_ids: list, device, target_label: int) -> float:
+    """Calculates and returns the Attack Success Rate of an Evasion Attack for an ASV model.
+    
+    Taken from the Security & Privacy of Machine Learning course (dr. Picek) and refactored."""
+    
+    correct = 0
+    total = 0
+    misclassifications = 0
+
+    with torch.no_grad():
+        asv_model.model.eval()
+
+        for utterance, speaker_id in tqdm(zip(perturbed_utterances, speaker_ids)):
+            # Use perturbed test image to get predictions of clean model
+            speaker_id = speaker_id.item()
+            utterance = utterance.to(device)
+            utterance = torch.squeeze(utterance)
+            utterance = torch.unsqueeze(utterance, 0)
+            
+            prediction = asv_model.get_speakers_using_waveforms(utterance)[0]
 
             # Check if the predicted speaker ID is equal to the target speaker ID
             if speaker_id != target_label:

### 2024-06-06 paper/paper.tex
Fixed that unholy grad bug I am euphoric

@@
 We run the PGD model for 10 steps.
-The implementation of the FGSM and PGD attacks is taken from the Torchattacks \citep{kim2020torchattacks} library and is refactored to fit our data.
+The implementation of the FGSM and PGD attacks is taken from the Torchattacks \citep{kim2020torchattacks} library and is refactored to better fit our needs.
 
 We use the evasion attacks to generate perturbed utterances with the speaker with ID 0 as the target.
-The perturbations should then move any audio file closer to the space of speaker ID 0 utterances.
-We feed these perturbed inputs to the ASV model, and measure its Speaker Identification Accuracy and Attack Success Rate.
-We also measure the clean ASR model's Word Error Rate on these perturbed inputs.
+This means that the perturbations caused by the attack should move any utterance closer to the space of utterances by the speaker with ID 0.
+We feed these perturbed inputs into the ASV model, and measure its Speaker Identification Accuracy and Attack Success Rate.
+We also measure the clean ASR model's WER on these perturbed inputs.
 
 \section{Results}
+The backdoored and perturbed utterances computed during the execution of the experiments have been saved as audio files.
+Examples of clean, JingleBack backdoored, FGSM perturbed, and PGD perturbed audio can be found at the following URL: \url{https://github.com/daanbrugmans/ru-automatic-speech-recognition-23-24/tree/main/audio}
+
 \subsection{Backdoor Attacks}

### 2024-06-06 code/ASR_2024_anonymization_module_learning/speaker_anonymization/spi.py

@@ -28,8 +28,8 @@ class SpeakerIdentificationModel:
         self.processor = Wav2Vec2Processor.from_pretrained(CONFIG.SPI_BACKBONE)
         self.model = Wav2Vec2Model.from_pretrained(CONFIG.SPI_BACKBONE).to(device)
 
-        for param in self.model.parameters():
-            param.requires_grad = False
+        # for param in self.model.parameters():
+        #     param.requires_grad = True
 
         self.classifier = nn.Linear(self.model.config.hidden_size, num_speakers).to(device)
         self.num_speakers = num_speakers
@@ -37,8 +37,8 @@ class SpeakerIdentificationModel:
         print(f"Initialized model with {num_speakers} speakers for fine-tuning.")
 
     def forward(self, input_values):
-        with torch.no_grad():
-            outputs = self.model(input_values.to(device))
+        # with torch.no_grad():
+        outputs = self.model(input_values.to(device))
         embeddings = outputs.last_hidden_state.mean(dim=1).to(device)
         logits = self.classifier(embeddings)
         return logits

### 2024-06-06 code/metrics.py

@@ -38,7 +38,7 @@ def attack_success_rate(asv_model: SpeakerIdentificationModel, adversarial_test_
                 
     return attack_success_rate, misclassifications
 
-def evasion_attack_success_rate(asv_model: SpeakerIdentificationModel, perturbed_utterances: list, speaker_ids: list, device, target_label: int) -> float:
+def evasion_attack_success_rate(asv_model, perturbed_utterances: list, speaker_ids: list, device, target_label: int) -> float:
     """Calculates and returns the Attack Success Rate of an Evasion Attack for an ASV model.
     
     Taken from the Security & Privacy of Machine Learning course (dr. Picek) and refactored."""

### 2024-06-06 paper/paper.tex
Finished the paper

@@
 \begin{abstract}
-
+  We explore potential weak points of a Speaker Anonymization system that uses a lightweight, digital effects-based pseudonymization strategy by adversarially attacking the neural speech models in the system used for evaluating the pseudonymization strategy.
+  We successfully insert a JingleBack backdoor into the system's Automatic Speaker Verification model, reaching an Attack Success Rate of 95\% after providing only 5 backdoored utterances.
+  We also show that the models are sensitive to FGSM and PGD attacks, and that small audio perturbations can lead to a remarkable decrease in model performance.
 \end{abstract}
@@
 \subsection{Neural Speaker Anonymization}
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.9\textwidth]{roddeman_etal_optimization.png}
+  \caption{The optimization process of the lightweight pseudonymization pipeline by \citet{roddeman2024anonymization}.}
+  \label{fig:roddeman_etal_optimization}
+\end{figure*}
+
 \citet{meyer2023anonymizing} showcase a successful realization of neural Speaker Anonymization using GANs.
@@
 
+\citet{kai2022lightweight} showcase a lightweight Speaker Anonymization pipeline.
+Their proposed pipeline pseudonymizes speech by applying voice modifications to the spoken utterances.
+In their pipeline, the authors make use of a neural ASR model alongside an \textit{Automatic Speaker Verification} (ASV) model, which are used for the recognition of words and speakers respectively.
+Instead of optimizing the performance of the ASR and ASV model, the authors attempt to optimize the voice modifications applied to the utterances.
+The optimization is performed by minimizing the \textit{Word Error Rate} (WER) and maximizing the \textit{Equal Error Rate} (EER).
+Figure \ref{fig:kai_etal_pipeline} shows the design of the proposed pipeline.
+
 \begin{figure}[h]
@@
 \end{figure}
-
-\citet{kai2022lightweight} showcase a lightweight Speaker Anonymization pipeline.
-Their proposed pipeline pseudonymizes speech by applying voice modifications to the spoken utterances.
-In their pipeline, the authors make use of a neural ASR model alongside an \textit{Automatic Speaker Verification} (ASV) model, which are used for the recognition of words and speakers respectively.
-Instead of optimizing the performance of the ASR and ASV model, the authors attempt to optimize the voice modifications applied to the utterances.
-The optimization is performed by minimizing the \textit{Word Error Rate} (WER) and maximizing the \textit{Equal Error Rate} (EER).
-Figure \ref{fig:kai_etal_pipeline} shows the design of the proposed pipeline.
 
@@
 Their pipeline uses the same optimization strategy used by \citeauthor{kai2022lightweight}: pre-trained ASR and ASV models are used to calculate the WER and EER, which are used to optimize a set of audio modifications for pseudonymization purposes.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.9\textwidth]{roddeman_etal_optimization.png}
-  \caption{The optimization process of the lightweight pseudonymization pipeline by \citet{roddeman2024anonymization}.}
-  \label{fig:roddeman_etal_optimization}
-\end{figure*}
 
@@
 
-\citet{goodfellow2015explaining} introduced FGSM, the \textit{Fast Gradient Sign Method}.
+\citet{goodfellow2015explaining} introduce FGSM, the \textit{Fast Gradient Sign Method}.
 FGSM perturbs an input by exploiting a trained model's gradients.
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.9\textwidth]{badnet.png}
+  \caption{An example of a BadNet attack \citep{gu2019badnets}.
+On the left, an image of a stop sign with varying BadNet backdoors can be seen.
+On the right, a backdoored network can be seen interpreting a stop sign as a speed limit sign due to the physical backdoor on the sign itself.}
+  \label{fig:badnet}
+\end{figure*}
+
 PGD's projection of an FGSM attack is performed by applying a clipping function $\text{clip}(\cdot)$ on the FGSM attack.
@@
 \subsubsection{Backdoor Attacks}
-\begin{figure*}[h]
-  \centering
-  \includegraphics[width=0.9\textwidth]{badnet.png}
-  \caption{An example of a BadNet attack \citep{gu2019badnets}.
-On the left, an image of a stop sign with varying BadNet backdoors can be seen.
-On the right, a backdoored network can be seen interpreting a stop sign as a speed limit sign due to the physical backdoor on the sign itself.}
-  \label{fig:badnet}
-\end{figure*}
-
 Backdoor attacks are adversarial attacks that are used during model training.
@@
 This means that the perturbations caused by the attack should move any utterance closer to the space of utterances by the speaker with ID 0.
-We feed these perturbed inputs into the ASV model, and measure its Speaker Identification Accuracy and Attack Success Rate.
+We feed these perturbed inputs into the ASV model, and measure its Speaker Identification Accuracy.
 We also measure the clean ASR model's WER on these perturbed inputs.
@@
 
+\subsection{Evasion Attacks}
+\begin{table}[h]
+    \centering
+    \begin{tabular}{c|c|c}
+        & \textbf{Acc} & \textbf{WER} \\
+        \hline
+        \textbf{Clean} & 0.62 & 0.104 \\
+        \textbf{FGSM} & 0.10 & 0.773 \\
+        \textbf{PGD} & 0.10 & 0.763
+    \end{tabular}
+    \caption{Scores of the Speaker Identification Accuracy (Acc) and Word Error Rate (WER) of the clean ASV and ASR models on unaltered/clean utterances, FGSM-perturbed utterances, and PGD-perturbed utterances from the test set.}
+    \label{tab:evasion_metrics}
+\end{table}
+
+The results of the FGSM and PGD attack experiments are shown in table \ref{tab:evasion_metrics}.
+After the utterances from the clean test set have been perturbed by an FGSM or PGD attack, the Speaker Identification Accuracy of the ASV model drops to 10\%.
+Since the ASV model predicts from a pool of ten speakers, its accuracy is now no better than random guesses.
+The ASR model's Word Error Rate has increased from 0.104 to 0.773 on FGSM-perturbed audio and 0.763 on PGD-perturbed audio.
+
 \section{Discussion}
-The results show that a simple JingleBack backdoor can successfully be inserted into \citeauthor{roddeman2024anonymization}'s ASV model using only 5 backdoored speech utterances, and that this number of backdoored utterances is sufficient in making the model misclassify 95\% of all utterances with the JingleBack trigger inserted.
+The results from the Backdoor Attack experiment show that a simple JingleBack backdoor can successfully be inserted into \citeauthor{roddeman2024anonymization}'s ASV model using only 5 backdoored speech utterances, and that this number of backdoored utterances is sufficient in making the model misclassify 95\% of all utterances with the JingleBack trigger inserted.
 The accuracy of the ASV model is not compromised as this backdoor is learned, with the ASV model being able to identify at least 80\% of all speakers correctly when given an utterance without the trigger, which is a higher accuracy than the clean ASV model.
@@
 
+The results from the Evasion Attacks experiment show that perturbing the utterances with an FGSM or PGD attack worsens the models' performances staggeringly: the FGSM attack causes the Word Error Rate to increase over sevenfold, and the Speaker Identification Accuracy is no better than purely random guesses.
+Despite its multi-step approach, the PGD attack causes the models to reach similar measures.
+It is likely that the perturbations, despite maximally deviating from the original utterances by a factor only of $\frac{8}{255}$, are too large for the models to handle.
+The size of the perturbations would prevent the generation of perturbed utterances that are still understandable by the models, which prevents an attacker from making the ASV model misclassify to a specific target speaker.
+However, the effects of the perturbations does show that the ASR and ASV models are quite sensitive to perturbed audio, which could be used to an attacker's advantage.
+
 \section{Conclusion}
@@
 We demonstrate that a pipeline that optimizes for lightweight effects-based speaker pseudonymization using neural speech models can be backdoored using a JingleBack attack, where the trigger is also another audio effect, and that such an attack can introduce a near-perfect backdoor into the neural models with as little as five adversarial examples.
-% Zeg ook nog een zin over evasion attacks.
+Furthermore, we demonstrate that the neural speech models are sensitive to FGSM-perturbed and PGD-perturbed audio, and that their performance drops remarkably once given utterances affected by an Evasion Attack.
+We conclude that adversarial attacks on Speaker Anonymization systems have the potential to disrupt the anonymization strategy and may prevent proper anonymization from being applied on spoken utterances.
 

### 2024-06-06 code/metrics.py

@@ -38,38 +38,6 @@ def attack_success_rate(asv_model: SpeakerIdentificationModel, adversarial_test_
                 
     return attack_success_rate, misclassifications
 
-def evasion_attack_success_rate(asv_model, perturbed_utterances: list, speaker_ids: list, device, target_label: int) -> float:
-    """Calculates and returns the Attack Success Rate of an Evasion Attack for an ASV model.
-    
-    Taken from the Security & Privacy of Machine Learning course (dr. Picek) and refactored."""
-    
-    correct = 0
-    total = 0
-    misclassifications = 0
-
-    with torch.no_grad():
-        asv_model.model.eval()
-
-        for utterance, speaker_id in tqdm(zip(perturbed_utterances, speaker_ids)):
-            # Use perturbed test image to get predictions of clean model
-            speaker_id = speaker_id.item()
-            utterance = utterance.to(device)
-            utterance = torch.squeeze(utterance)
-            utterance = torch.unsqueeze(utterance, 0)
-            
-            prediction = asv_model.get_speakers_using_waveforms(utterance)[0]
-
-            # Check if the predicted speaker ID is equal to the target speaker ID
-            if speaker_id != target_label:
-                total += 1
-                
-                if prediction == target_label:
-                    correct += 1
-
-    attack_success_rate = correct / total    
-                
-    return attack_success_rate, misclassifications
-
 def clean_accuracy_drop(clean_model: SpeakerIdentificationModel, adversarial_model: SpeakerIdentificationModel, clean_test_set: Dataset) -> float:
     """Calculates and returns the Clean Accuracy Drop between a clean and adversarial ASV model."""
     

### 2024-06-06 code/ASR_2024_anonymization_module_learning/speaker_anonymization/config.py
Tidied up code

@@ -38,6 +38,7 @@ class Config:
     CACHE_FOLDER = "d:/Datasets/vctk/cache"#"cache"
     ANONYMIZED_FOLDER = "d:/Datasets/vctk/anonymized_audio"
     BACKDOORED_FOLDER = "d:/Datasets/vctk/backdoored_audio"
+    PERTURBED_FOLDER = "d:/Datasets/vctk/perturbed_audio"
     SHOW_PROGRESS_BAR = False
     CONFIG_N_JOBS = 1  # Number of jobs to run in parallel, -1 means use all
     SEED = 3131

### 2024-06-06 code/ASR_2024_anonymization_module_learning/speaker_anonymization/spi.py

@@ -27,17 +27,12 @@ class SpeakerIdentificationModel:
         self.study_name = CONFIG.STUDY_NAME
         self.processor = Wav2Vec2Processor.from_pretrained(CONFIG.SPI_BACKBONE)
         self.model = Wav2Vec2Model.from_pretrained(CONFIG.SPI_BACKBONE).to(device)
-
-        # for param in self.model.parameters():
-        #     param.requires_grad = True
-
         self.classifier = nn.Linear(self.model.config.hidden_size, num_speakers).to(device)
         self.num_speakers = num_speakers
         self.resampler = T.Resample(orig_freq=48000, new_freq=16000)
         print(f"Initialized model with {num_speakers} speakers for fine-tuning.")
 
     def forward(self, input_values):
-        # with torch.no_grad():
         outputs = self.model(input_values.to(device))
         embeddings = outputs.last_hidden_state.mean(dim=1).to(device)
         logits = self.classifier(embeddings)

### 2024-06-06 code/attacks/fgsm.py

@@ -1,6 +1,3 @@
-from ASR_2024_anonymization_module_learning.speaker_anonymization.spi import SpeakerIdentificationModel
-from ASR_2024_anonymization_module_learning.speaker_anonymization.losses import speaker_verification_loss
-
 import torch
 import torch.nn as nn
 
@@ -12,60 +9,49 @@ class FGSM(EvasionAttack):
     FGSM in the paper 'Explaining and harnessing adversarial examples'
     [https://arxiv.org/abs/1412.6572]
 
-    Distance Measure : Linf
-
-    Arguments:
-        model (nn.Module): model to attack.
-        eps (float): maximum perturbation. (Default: 8/255)
-
-    Shape:
-        - images: :math:`(N, C, H, W)` where `N = number of batches`, `C = number of channels`,        `H = height` and `W = width`. It must have a range [0, 1].
-        - labels: :math:`(N)` where each value :math:`y_i` is :math:`0 \leq y_i \leq` `number of labels`.
-        - output: :math:`(N, C, H, W)`.
-
-    Examples::
-        >>> attack = torchattacks.FGSM(model, eps=8/255)
-        >>> adv_images = attack(images, labels)
-
     Taken from the Torchattacks (https://arxiv.org/abs/2010.01950) library and refactored."""
 
-    def __init__(self, asv_model: SpeakerIdentificationModel, eps=8 / 255):
+    def __init__(self, asv_model, eps=8/255):
         super().__init__("FGSM", asv_model.model)
         self.eps = eps
         self.supported_mode = ["default", "targeted"]
-        self.asv_model = asv_model
+        self.processor = asv_model.processor
+        self.classifier = asv_model.classifier
 
-    def forward(self, utterances, labels):
+    def forward(self, utterance, label):
         r"""
         Overridden.
         """
-
-        utterances = utterances.clone().detach().to(self.device)
-        labels = labels.clone().detach().to(self.device)
-
-        if self.targeted:
-            target_labels = self.get_target_label(utterances, labels)
-
-        # loss = nn.CrossEntropyLoss()
-
-        utterances.requires_grad = True
-        # outputs = self.get_logits(images)
-        outputs = self.asv_model.get_speakers_using_waveforms(utterances)
-
+        
+        torch.cuda.empty_cache()
+        
+        utterance = torch.unsqueeze(utterance, dim=0)
+        utterance = utterance.to(self.device)
+        utterance.requires_grad = True
+        
[…]

### 2024-06-06 code/attacks/jingleback.py

@@ -1,7 +1,7 @@
 from attacks.backdoor_attack import BackdoorAttack
 
 import torch
-from pedalboard import Pedalboard, LadderFilter, Gain, Phaser
+from pedalboard import Pedalboard, LadderFilter
 
 class JingleBack(BackdoorAttack):
     def __init__(self, source_label = int, target_label = int) -> None:

### 2024-06-06 code/attacks/pgd.py

@@ -9,72 +9,65 @@ class PGD(EvasionAttack):
     PGD in the paper 'Towards Deep Learning Models Resistant to Adversarial Attacks'
     [https://arxiv.org/abs/1706.06083]
 
-    Distance Measure : Linf
+    Taken from the Torchattacks (https://arxiv.org/abs/2010.01950) library and refactored."""
 
-    Arguments:
-        model (nn.Module): model to attack.
-        eps (float): maximum perturbation. (Default: 8/255)
-        alpha (float): step size. (Default: 2/255)
-        steps (int): number of steps. (Default: 10)
-        random_start (bool): using random initialization of delta. (Default: True)
-
-    Shape:
-        - images: :math:`(N, C, H, W)` where `N = number of batches`, `C = number of channels`,        `H = height` and `W = width`. It must have a range [0, 1].
-        - labels: :math:`(N)` where each value :math:`y_i` is :math:`0 \leq y_i \leq` `number of labels`.
-        - output: :math:`(N, C, H, W)`.
-
-    Examples::
-        >>> attack = torchattacks.PGD(model, eps=8/255, alpha=1/255, steps=10, random_start=True)
-        >>> adv_images = attack(images, labels)
-
-    """
-
-    def __init__(self, model, eps=8 / 255, alpha=2 / 255, steps=10, random_start=True):
-        super().__init__("PGD", model)
+    def __init__(self, asv_model, eps=8/255, alpha=2/255, steps=10, random_start=True):
+        super().__init__("FGSM", asv_model.model)
+        self.eps = eps
         self.eps = eps
         self.alpha = alpha
         self.steps = steps
         self.random_start = random_start
         self.supported_mode = ["default", "targeted"]
+        self.processor = asv_model.processor
+        self.classifier = asv_model.classifier
 
-    def forward(self, images, labels):
+    def forward(self, utterance, label):
         r"""
         Overridden.
         """
-
-        images = images.clone().detach().to(self.device)
-        labels = labels.clone().detach().to(self.device)
-
-        if self.targeted:
-            target_labels = self.get_target_label(images, labels)
-
-        loss = nn.CrossEntropyLoss()
-        adv_images = images.clone().detach()
+        
+        torch.cuda.empty_cache()
+        
+        utterance = torch.unsqueeze(utterance, dim=0)
+        utterance = utterance.to(self.device)
+        utterance.requires_grad = True
+        
[…]

### 2024-06-06 code/backdoored_dataset.py

@@ -4,12 +4,9 @@ from ASR_2024_anonymization_module_learning.speaker_anonymization.config import 
 
 from attacks.backdoor_attack import BackdoorAttack
 
-import datasets.load
-
 import torchaudio
 from torch.utils.data import Dataset
 from torch.utils.data import DataLoader
-from torch.utils.data import random_split
 
 class BackdooredVCTK(Dataset):
         def __init__(self, backdoor: BackdoorAttack, poisoning_rate: float, train: bool, pipeline_config: Config) -> None:
@@ -88,24 +85,3 @@ class CachedVCTK(Dataset):
     
     def __getitem__(self, index):
         return (self.utterances[index], self.speaker_ids[index], self.transcriptions[index], self.sample_rates[index], self.file_paths[index])
-    
-                
-def get_dataloaders(backdoor: BackdoorAttack = None, train_split=0.8) -> tuple[DataLoader, DataLoader, DataLoader]:
-    """Returns DataLoader objects for a train, validation, and test set of the dataset. If an `Attack` object is passed, it will backdoor the data using the object first."""
-    
-    if backdoor is None:
-        dataset_train_val = datasets.load.load_dataset("vctk", split="train", cache_dir="d:/Datasets/vctk/cache")
-        dataset_test = datasets.load.load_dataset("vctk", split="train", cache_dir="d:/Datasets/vctk/cache")
-    else:
-        dataset_train_val = BackdooredVCTK(backdoor, train=True)
-        dataset_test = BackdooredVCTK(backdoor, train=False)
-    
-    train_size = int(len(dataset_train_val) * train_split)
-    val_size = int(len(dataset_train_val) - train_size)
-    dataset_train, dataset_val = random_split(dataset_train_val, [train_size, val_size])
-    
-    dataloader_train = DataLoader(dataset_train, batch_size=128, shuffle=True)
-    dataloader_val = DataLoader(dataset_val, batch_size=128, shuffle=False)
-    dataloader_test = DataLoader(dataset_test, batch_size=128, shuffle=False)
-    
-    return dataloader_train, dataloader_val, dataloader_test

### 2024-06-06 code/neural_model.py

@@ -1,174 +1,0 @@
-from attacks.backdoor_attack import BackdoorAttack
-from backdoored_dataset import get_dataloaders
-
-import matplotlib.pyplot as plt
-import numpy as np
-import sklearn
-from tqdm import tqdm
-
-import torch
-from torch import nn
-
-class NeuralModel:
-    def __init__(self, device, epochs: int = 30, attack: BackdoorAttack = None) -> None:
-        self.neural_network = ....to(device)
-        self.loss_function = ...
-        self.optimizer = torch.optim.AdamW(self.neural_network.parameters(), lr=0.001)
-        self.epochs = epochs
-        self.device = device
-        
-        if attack is None:
-            self.train_data, self.val_data, self.test_data = get_dataloaders()
-            self.attack = None
-        else:
-            self.train_data, self.val_data, self.test_data = get_dataloaders(backdoor=attack)
-            self.attack = attack
-        
-        self.history = None
-        
-    def train(self):
-        """Train the network."""
-        
-        # Keep record of loss and accuracy metrics for most recent training procedure
-        self.history = {
-            "Train Type": "Clean" if self.attack is None else f"Adversarial ({self.attack.attack_name})",
-            "Train Loss": [],
-            "Validation Loss": [],
-            "Train Accuracy": [],
-            "Validation Accuracy": []
-        }
-        
-        for epoch in range(self.epochs):
-            print(f"Started Epoch {epoch + 1}")
-            
-            self.neural_network.train()
-            
-            # Train
-            print(" Training...")
-            
-            train_batch_losses = []
-            train_batch_accuracies = []
-            
-            for images, targets in tqdm(self.train_data):
-                images = images.to(self.device)
-                targets = targets.to(self.device)
-                
-                predictions = self.neural_network(images)
-                
-                # Calculate train loss and backpropagate
-                train_batch_loss = self.loss_function(predictions, targets)
-                train_batch_losses.append(train_batch_loss)
-                train_batch_loss.backward()
-                
-                # Move predictions and labels to cpu for accuracy calculation
-                predictions = torch.max(predictions, dim=1)[1]
-                predictions = predictions.cpu().detach().numpy()
-                targets = targets.cpu().detach().numpy()
-                
-                # Calculate train accuracy
-                train_batch_accuracy = sklearn.metrics.accuracy_score(y_pred=predictions, y_true=targets)
-                train_batch_accuracies.append(train_batch_accuracy)
-                
[…]
